---
output:
  html_document: default

title: "Atlas of distant water fishing - Analysis"
author: "Matthew Warham, Kat Millage"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
---

# Introduction

This script pulls information on fishing effort from Global Fishing Watch for distant water fishing vessels. The top countries with distant water fishing fleets and the top EEZs with the most distant water fishing activity are then identified.  

```{r setup, include=FALSE}
# Chunk options
knitr::opts_chunk$set(echo = TRUE)

### Load packages ------
library(sf) # spatial manipulation
library(lwgeom) # needed for curved lines
library(here) # path names
library(knitr) # knit document
library(bigrquery) # access GFW data
library(DBI) # access GFW data
library(countrycode) # country names 
library(tidyverse) # data manipulation
library(ggalt) # transform to robinson projection
library(RColorBrewer) # custom color palettes
library(scales) # scales for plotting
library(ggpubr) # plot arranging
library(gridExtra)
library(grid)
library(png)

### Set run options -----

# Run flag state analysis (T/F)?
run_flag_state <- F
# Set purpose of the flag state analysis (currently the only choice is "top_ranked")
flag_state_purpose <- "top_ranked"
# Number of flag_states to include (only necessary if purpose is "top_ranked", defaults to 10)
number_of_top_countries_flag <- 20

# Run EEZ analysis (T/F)?
run_eez <- T
# Set purpose of the EEZ anlysis (choices: "ACP" or "top_ranked", defaults to "top_ranked")
eez_purpose <- "ACP"
# Number of EEZs to include (only necessary if purpose is "top_ranked", defaults to 10)
number_of_top_countries_eez <- 10

# Connection to BigQuery - need a project for billing
bq_project <-  "ucsb-gfw"
# Do you want to pull fresh data from GFW?
rerun_gfw <- T

# Choose analysis year (2012 - 2018)
analysis_year <- 2018

```


```{r}
### Create results directories -----
# Shouldn't need to manually change anything in this section

# If either the flag state or eez analyses should be run: 
if(run_flag_state | run_eez){
  
  # Set general results directory
  results_dir <- here::here("results/")
  if (dir.exists(results_dir) == F) { dir.create(results_dir, recursive = T) }
  
  ## Create flag state results directories
  if(run_flag_state){
    
    flag_state_results_dir <- paste0(results_dir, "flag_state_results/", flag_state_purpose, "/")
    if (dir.exists(flag_state_results_dir) == F) { dir.create(flag_state_results_dir, recursive = T) }

    flag_state_country_dat_dir <- paste0(flag_state_results_dir, "country_dat/")
    if (dir.exists(flag_state_country_dat_dir) == F) { dir.create(flag_state_country_dat_dir, recursive = T) }

    flag_state_figures_dir <- paste0(flag_state_results_dir, "figures/")
    if (dir.exists(flag_state_figures_dir) == F) { dir.create(flag_state_figures_dir, recursive = T) }

    flag_state_pdf_dir <- paste0(flag_state_results_dir, "pdfs/")
    if (dir.exists(flag_state_pdf_dir) == F) { dir.create(flag_state_pdf_dir, recursive = T) }
    
  } # /flag state results
  
  ## Create eez results directories
  if(run_eez){
    
    eez_results_dir <- paste0(results_dir, "eez_results/", eez_purpose, "/")
    if (dir.exists(eez_results_dir) == F) { dir.create(eez_results_dir, recursive = T) }
    
    eez_dat_dir <- paste0(eez_results_dir, "dat/")
    if (dir.exists(eez_dat_dir) == F) { dir.create(eez_dat_dir, recursive = T) }

    eez_figures_dir <- paste0(eez_results_dir, "figures/")
    if (dir.exists(eez_figures_dir) == F) { dir.create(eez_figures_dir, recursive = T) }

    eez_pdf_dir <- paste0(eez_results_dir, "pdfs/")
    if (dir.exists(eez_pdf_dir) == F) { dir.create(eez_pdf_dir, recursive = T) }
    
    
    # If EEZ purpose is "ACP", also create a results directory for the app
    if(eez_purpose == "ACP"){
      eez_results_app_dir <- paste0(here::here("SubsidyAtlasACP/"), "data/eez_results/", eez_purpose, "/")
      if (dir.exists(eez_results_app_dir) == F) { dir.create(eez_results_app_dir, recursive = T) }
    }
    
  } # /eez results
  
} # /all results
```

## Flag state and EEZ centroids 

In order to make our connection plots, we need to find the centroids of each EEZ and flag state so we can create the connectivity lines. For the flag state analysis and the eez analyis for the top ranked EEZs, we're going to use a standard -180 to 180 degree world view for plotting to keep things simple. 

Things get slightly more complicated for the ACP eez analysis because we want to use three different world views for each of the three regions (so the region of interest is centered). Therefore we have created shapefiles that span from -360 to 360 degrees, which we can clip to the appropriate extents for each of our three regions (Africa, Caribbean, and Pacific). For Africa, we've chosen to use a -180 to 180 degree view (so we'll also use this for the flag state analysis and/or the top ranked eez analysis). For the Caribbean, we've chosen to use a -260 to 100 degree view. For the Pacific, we've chosen to use a 0 to 360 degree view. 

For the purposes of plotting the EEZs in which the fishing activity is taking place, we're using a simplified form of the Version 10 shapefile of the Maritime Boundaries - World EEZs from MarineRegions.org. We simplified the shapefile using mapshaper (online at mapshaper.org) to a tolerance of 0.5%. For the purposes of plotting the flag states to which distant water vessels are flagged, we're using the Version 2 shapefile of the Marine and land zones: the union of world country boundaries and EEZs from Marine Regions.org.

```{r}
# For the flag state analysis and the eez analysis for the top ranked EEZs we're going to use the standard -180 to 180 degree world view
# For the ACP analysis, things get a little complicated as we want to use three different world views for the three different regions
# For Africa, we're going to use the standard -180 to 180 degree world view
# For the Pacific, we're going to use a 0 to 360 degree world view
# For the Caribbean, we're going to use a -260 to 100 degree world view
# Therefore, if we're running the flag state analysis, or the top-ranked EEZ analysis, we'll just use the coordinates for the Africa version
if(run_flag_state | run_eez){
  
  ### EEZs for location of fishing activity -----
  eez_map <- read_sf(dsn = here::here("SubsidyAtlasACP", "data", "shapefiles_edit", "World_EEZ_v10_20180221_LR_-360_360"), layer = "eez_v10") %>%
    st_transform(crs = 4326) %>%
    setNames(tolower(names(.))) %>%
    dplyr::select(id = cat,
                  mrgid,
                  geoname,
                  pol_type,
                  territory1,
                  iso3_ter1 = iso_ter1,
                  sovereign1,
                  territory2,
                  iso3_ter2 = iso_ter2,
                  sovereign2,
                  territory3,
                  iso3_ter3 = iso_ter3,
                  sovereign3)
  
  # Pacific
  pacific_eez_map <- st_crop(eez_map, c(xmin=0, xmax=360, ymin=-90, ymax=90))
  pacific_eez_map_centroids <- pacific_eez_map %>%
    st_centroid() %>%
    dplyr::select(eez_code = mrgid, eez_name = geoname, geometry) %>%
    mutate(region = "Pacific")
  
  # Africa
  africa_eez_map <- st_crop(eez_map, c(xmin=-180, xmax=180, ymin=-90, ymax=90))
  africa_eez_map_centroids <- africa_eez_map %>%
    st_centroid() %>%
    dplyr::select(eez_code = mrgid, eez_name = geoname, geometry) %>%
    mutate(region = "Africa")
  
  # Caribbean
  caribbean_eez_map <- st_crop(eez_map, c(xmin=-180, xmax=180, ymin=-90, ymax=90))
  caribbean_eez_map_centroids <- caribbean_eez_map %>%
    st_centroid() %>%
    dplyr::select(eez_code = mrgid, eez_name = geoname, geometry) %>%
    mutate(region = "Caribbean")
  
  # Bind together 
  eez_map_centroids <- pacific_eez_map_centroids %>%
    rbind(africa_eez_map_centroids) %>%
    rbind(caribbean_eez_map_centroids)
  
  # Put centroids in lon/lat columns
  eez_map_centroid_coordinates <- tibble(eez_code = eez_map_centroids$eez_code,
                                         eez_name = eez_map_centroids$eez_name,
                                         region = eez_map_centroids$region) %>% 
    bind_cols(do.call(rbind, st_geometry(eez_map_centroids)) %>%
                as_tibble() %>%
                setNames(c("eez_lon", "eez_lat"))) %>%
    arrange(eez_code)
  
  ### Combined land/EEZs for flag states -----
  land_eez_map <- read_sf(dsn = here::here("SubsidyAtlasACP", "data", "shapefiles_edit", "EEZ_land_v2_201410_-360_360"), layer = "EEZ_land_v2_201410_-360_360") %>%
    st_transform(crs = 4326) %>%
    setNames(tolower(names(.))) %>%
    dplyr::select(id = objectid,
                  iso3 = iso_3digit,
                  country)
  
   # Pacific
  pacific_land_eez_map <- st_crop(land_eez_map, c(xmin=0, xmax=360, ymin=-90, ymax=90))
  pacific_land_eez_map_centroids <- pacific_land_eez_map %>%
    st_centroid() %>%
    dplyr::select(flag = iso3, flag_name = country, geometry) %>%
    mutate(region = "Pacific")
  
  # Africa
  africa_land_eez_map <- st_crop(land_eez_map, c(xmin=-180, xmax=180, ymin=-90, ymax=90))
  africa_land_eez_map_centroids <- africa_land_eez_map %>%
    st_centroid() %>%
    dplyr::select(flag = iso3, flag_name = country, geometry) %>%
    mutate(region = "Africa")
  
  # Caribbean
  caribbean_land_eez_map <- st_crop(land_eez_map, c(xmin=-180, xmax=180, ymin=-90, ymax=90))
  caribbean_land_eez_map_centroids <- caribbean_land_eez_map %>%
    st_centroid() %>%
    dplyr::select(flag = iso3, flag_name = country, geometry) %>%
    mutate(region = "Caribbean")
  
  # Bind together
  land_eez_map_centroids <- pacific_land_eez_map_centroids %>%
    rbind(africa_land_eez_map_centroids) %>%
    rbind(caribbean_land_eez_map_centroids)
  
  
  
  # Put centroids in lon/lat columns
  land_eez_map_centroid_coordinates <- tibble(flag = land_eez_map_centroids$flag,
                                              flag_name = land_eez_map_centroids$flag_name,
                                              region = land_eez_map_centroids$region) %>% 
    bind_cols(do.call(rbind, st_geometry(land_eez_map_centroids)) %>%
                as_tibble() %>%
                setNames(c("flag_lon", "flag_lat"))) %>%
    arrange(flag) %>%
    na.omit()
  
   #Manually correct certain centroids
   manual_coordinates_flags <- read_csv(paste0(results_dir, "corrected_flag_centroids.csv"))
   
   land_eez_map_centroid_coordinates <- land_eez_map_centroid_coordinates %>%
     left_join(manual_coordinates_flags, by = c("flag", "region")) %>%
     mutate(flag_lon = ifelse(!is.na(flag_lon_edit), flag_lon_edit, flag_lon),
            flag_lat = ifelse(!is.na(flag_lat_edit), flag_lat_edit, flag_lat)) %>%
     dplyr::select(-flag_lon_edit, -flag_lat_edit)

}
```

We also need to do some setup for our figures. 

```{r}
if(run_flag_state | run_eez){
  
  # Custom theme for map
  maptheme <- theme_minimal() +
    theme(panel.background = element_rect(fill = "grey27", colour = NA),
          panel.grid.major = element_line(colour = "grey27"),
          panel.border = element_blank(),
          plot.margin = unit(c(0, 0, 0, 0), "mm"),
          plot.background = element_blank(),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks.length = unit(0, "pt"))

}
if(run_flag_state){
  
  # Custom color palette for Sumaila subsidy types
  goodColors <- rev(brewer.pal(3, "Blues"))
  names(goodColors) <- levels(subsidy_dat_edit$type)[1:3]
  
  badColors <- rev(brewer.pal(7, "Reds"))
  names(badColors) <- levels(subsidy_dat_edit$type)[4:10]
  
  ambigColors <- c("purple", "mediumorchid", "violet")
  names(ambigColors) <- levels(subsidy_dat_edit$type)[11:13]
  
  myColors <- c(goodColors, badColors, ambigColors)

}
```

## Part 1: Identify top DW fishing fleets by flag state

Currently, the only option for this part of the analysis is to look at distant water fishing fleets by flag state, ranked according to total distant water fishing effort. 

We first rank flag states with DW fishing fleets based on the following metrics:
- Number of fishing vessels partaking in DW fishing
- Total capacity of fishing vessels partaking of DW fishing
- Total number of DW fishing hours
- Total number of DW fishing KWh 

```{r}
if(run_flag_state){

# Mutate totals by flag state for all
flag_state_ranking <- dw_effort_final_manual %>% 
  group_by(flag, ssvid) %>%
  summarize(engine_power_kw = unique(engine_power_kw),
            fishing_hours = sum(fishing_hours_year_eez, na.rm = T),
            fishing_KWh = sum(fishing_KWh_year_eez, na.rm = T)) %>%
  ungroup() %>%
  group_by(flag) %>%
  summarize(total_vessels = n_distinct(ssvid),
            total_capacity = sum(engine_power_kw, na.rm = T),
            total_fishing_hours = sum(fishing_hours, na.rm = T),
            total_fishing_KWh = sum(fishing_KWh, na.rm = T)) %>% 
  arrange(desc(total_vessels)) %>%
  ungroup() %>%
  mutate(vessel_rank = dense_rank(desc(total_vessels)),
         capacity_rank = dense_rank(desc(total_capacity)),
         fishing_hours_rank = dense_rank(desc(total_fishing_hours)),
         fishing_KWh_rank = dense_rank(desc(total_fishing_KWh))) %>%
  mutate(avg_rank = rowMeans(select(., c(vessel_rank, capacity_rank, fishing_hours_rank, fishing_KWh_rank))))

# Save flag states by average ranking
write_csv(flag_state_ranking, paste0(flag_state_results_dir, "flag_state_ranking_", analysis_year, ".csv"))

}
```

We then identify the top `r number_of_top_countries_flag` flag states. For each of our top flag states, we also identify all EEZs in which DW vessels flagged to that state fish.

```{r}
if(run_flag_state){
  
  # Set defaults in case option isn't correctly specified above
  if(is.na(number_of_top_countries_flag) | !is.numeric(number_of_top_countries_flag)){
    number_of_top_countries_flag <- 10
  }

  flag_state_ranking_top <- flag_state_ranking %>%
    top_n(-number_of_top_countries_flag, wt = avg_rank)
  
  # Get iso3 codes for selected flag states 
  top_flag_states <- flag_state_ranking_top$flag

  top_flag_states_names <- (tibble(flag = top_flag_states) %>%
    mutate(name = countrycode::countrycode(flag, "iso3c", "country.name")))$name

  flag_state_combinations <- dw_effort_final_manual %>%
    dplyr::filter(flag %in% top_flag_states) %>%
    group_by(flag, eez_code = as.numeric(eez_code)) %>%
    summarize(vessels = n_distinct(ssvid),
              capacity = sum(engine_power_kw, na.rm = T),
              fishing_h = sum(fishing_hours_year_eez, na.rm = T),
              fishing_KWh = sum(fishing_KWh_year_eez, na.rm = T)) %>%
    arrange(flag) %>%
    ungroup() %>%
    mutate(region == "Africa")

}
```

We then match the previously obtained centroids to each of our top flag states, as well as all EEZs in which DW vessels from these states fish. 

```{r}
if(run_flag_state){
  
flag_state_mapping <- flag_state_combinations %>%
  left_join(land_eez_map_centroid_coordinates, by = c("flag" = "flag", "region" = "region")) %>%
  left_join(eez_map_centroid_coordinates, by = c("eez_code" = "eez_code", "region" = "region"))
  
flag_state_mapping_wlines <- flag_state_mapping %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(flag_state_mapping) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326) %>%
  mutate(fishing_KWh = round(fishing_KWh, digits = 4))

st_write(flag_state_mapping_wlines, dsn = paste0(flag_state_results_dir, "flag_state_mapping_with_lines.shp"),  delete_dsn=TRUE, driver = "ESRI Shapefile")

}
```

We then make our connectivity maps and subsidy plots for each of our top ranked flag states. 

```{r}
if(run_flag_state){
  
## For loop to run top X countries
for(i in 1:length(top_flag_states)){
   
### Step 1: Flag state connectivity data
# Pull connectivity data for only our flag state of interest
flag_dat <- flag_state_mapping_wlines %>%
  dplyr::filter(flag == top_flag_states[i]) 

# Write flag state connectivity data
write_csv(flag_dat, path = paste0(flag_state_country_dat_dir, top_flag_states[i], "_flag_state_dat.csv"))

### Step 2: Make connectivity map
# Map
map_plot <- ggplot()+
  geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = country_map %>% dplyr::filter(iso3 == top_flag_states[i]), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, white border lines)
  geom_sf(data = EEZ_map %>% dplyr::filter(iso_tr1 == top_flag_states[i]), fill = NA, alpha = 0.5, color = NA, size = 0.1) +
  geom_sf(data = EEZ_map %>% dplyr::filter(mrgid %in% flag_dat$eez_code), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = flag_dat, col = "darkgoldenrod", size = 0.25) + 
  maptheme+
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

# Save map
ggsave(map_plot, filename = paste0(flag_state_figures_dir, top_flag_states[i], "_flag_state_map.png"), width = 10, units = "in")

# Combine map into a one page pdf
sfg_logo_white <- readPNG(here::here("common", "sfg-logo-white.png"))
logo_white <- rasterGrob(sfg_logo_white, interpolate=TRUE, vjust = 0.8, hjust = 0.6)

title1 <- textGrob(paste0("Global network of distant-water fishing\nFlag state: ", top_flag_states_names[i]), gp = gpar(fontsize=16, fontface="bold", lineheight=1, col = "white", fontfamily = "Helvetica"), hjust = 0.55, vjust = 1)

caption1 <- textGrob(paste0("This map shows the global range of distant-water fishing effort for vessels flagged to ", top_flag_states_names[i], ". Lines connect the flag state (pink) \nwith all foreign EEZs (blue) in which vessels flagged to that state fished in 2018. Data were taken from Global Fishing Watch (2018)."), gp = gpar(fontsize = 10, col = "white", fontfamily = "Helvetica"), vjust = 0, hjust = 0.5)

lay1 <- rbind(c(1,4),
              c(2,2),
              c(2,2),
              c(3,3))

# Put together connectivity map
map_page <- grid.arrange(title1, map_plot, caption1, logo_white,
                         layout_matrix = lay1,
                         heights=unit(c(1,1.5,5,1), c("in")), 
                         widths=unit(c(8,3), "in"))
out1 <- cowplot::ggdraw(map_page) + 
  theme(plot.background = element_rect(fill="grey27", color = NA))

# Save connectivity map
ggsave(out1, filename = paste0(flag_state_pdf_dir, top_flag_states[i], "_map_page.pdf"), width = 11, height = 8.5, units = "in")

### Step 3: Make fisheries subsidies summary plot(s) 
# Subsidies by subtype plot
flag_subsidy_dat <- subsidy_dat_ordered %>%
  dplyr::filter(iso3 == top_flag_states[i]) %>%
  na.omit()

if(nrow(flag_subsidy_dat) > 0){
  
  # Filter color scale to only use those for subsidy types represented by that country
  filtered_colors <- myColors[names(myColors) %in% unique(flag_subsidy_dat$type)]
  
  # Make plot
  subsidy_plot <- ggplot(flag_subsidy_dat, aes(x = category, y = value/1e6, fill = type))+
    geom_bar(stat = "identity")+
    scale_fill_manual(name = "Subsidy Type", values = filtered_colors, labels = unique(flag_subsidy_dat$type))+
    theme_bw()+
    coord_flip()+
    scale_y_continuous(expand = c(0,0), labels = scales::comma)+
    labs(x = "", y = "Est. fisheries subsidies (2018 $USD, millions)")
  
  # Save plot as png
  ggsave(subsidy_plot, filename = paste0(flag_state_figures_dir, top_flag_states[i], "_subsidy_plot.png"), width = 10, height = 6, units = "in")
  
  # Make one page pdf of subsidy/other statistics
  sfg_logo_black <- readPNG(here::here("common", "sfg-logo-black.png"))
  logo_black <- rasterGrob(sfg_logo_black, interpolate=TRUE, vjust = 0.8, hjust = 0.6)

  title2 <- textGrob(paste0("Global network of distant-water fishing\nFlag state: ", top_flag_states_names[i]), gp = gpar(fontsize=16, fontface="bold", lineheight=1, col = "black", fontfamily = "Helvetica"), hjust = 0.55, vjust = 1)
  
  dw_summary <- textGrob(
    paste0("Number of distant-water vessels: ", format(flag_state_ranking_top$total_vessels[i], big.mark = ","), 
           "  |  Rank: ", flag_state_ranking_top$vessel_rank[i],
           "\nNumber of EEZs fished: ", length(unique(flag_dat$eez_code)), 
           # "  |  Rank: ", flag_state_combinations_ranking$eez_rank[flag_state_combinations_ranking$flag == top_flag_states[i]],
           "\nTotal distant-water capacity (KW): ", format(round(flag_state_ranking_top$total_capacity[i]), big.mark = ","),
           "  |  Rank: ", flag_state_ranking_top$capacity_rank[i],
           "\nTotal distant-water fishing effort (hours): ", format(round(flag_state_ranking_top$total_fishing_hours[i]), big.mark = ","),
           "  |  Rank: ", flag_state_ranking_top$fishing_hours_rank[i],
           "\nTotal distant-water fishing effort (KWh): ", format(round(flag_state_ranking_top$total_fishing_KWh), big.mark = ","),
           "  |  Rank: ", flag_state_ranking_top$fishing_KWh_rank[i]), just = "left", x = unit(0.14, "npc")
  )

  caption2 <- textGrob(paste0("This figure shows fisheries subsides provided by ", top_flag_states_names[i], " in 2018 $USD. Subsidies are grouped into three types: neutral (purples), capacity-enhancing (reds), \nand beneficial (blues) based on their generalized effects. Data are updated estimates from those found in Sumaila et al. (2016)."), gp = gpar(fontsize = 10, col = "black", fontfamily = "Helvetica"), vjust = 0, hjust = 0.5)

  # Layout matrix
  lay <- rbind(c(1,5),
               c(2,2),
               c(3,3),
               c(4,4))
  
  # Create info/summary page
info_page <- grid.arrange(title2, dw_summary, subsidy_plot, caption2, logo_black, 
                          layout_matrix = lay, 
                          heights = unit(c(1,1.5,5,1), "in"), 
                          widths = unit(c(8,3), "in"))

out2 <- cowplot::ggdraw(info_page) +
  theme(plot.background = element_rect(fill="white", color = NA))

# Save summary page
ggsave(out2, filename = paste0(flag_state_pdf_dir, top_flag_states[i], "_info_page.pdf"), width = 11, height = 8.5, units = "in")
  
# Save both plots into one pdf
  out_flag_state <- marrangeGrob(grobs = list(out1, out2), nrow = 1, ncol = 1, top = NULL)
  
  ggsave(out_flag_state, filename = paste0(flag_state_pdf_dir, top_flag_states[i], "_combined.pdf"), width = 11, height = 8.5, units = "in")
}
}
}
```


## Part 2: Identify top locations of DW fishing by EEZ

If the purpose of the eez analysis is to identify the top `r number_of_top_countries_eez` EEZs in which DW fleets fish, we consider the following metrics:
- Number of fishing vessels partaking in DW fishing
- Total number of DW fishing hours
- Total number of DW fishing KWh

```{r}
if(run_eez){
# Mutate totals by EEZ
EEZ_ranking <- dw_effort_final_manual %>% 
  group_by(eez_code, eez_name, eez_territory_iso3, eez_sovereign_iso3, ssvid) %>%
  summarize(engine_power_kw = unique(engine_power_kw),
            fishing_hours = sum(fishing_hours_year_eez, na.rm = T),
            fishing_KWh = sum(fishing_KWh_year_eez, na.rm = T)) %>%
  ungroup() %>%
  group_by(eez_code, eez_name, eez_territory_iso3, eez_sovereign_iso3) %>%
  summarize(total_vessels = n_distinct(ssvid),
            total_capacity = sum(engine_power_kw, na.rm = T),
            total_fishing_hours = sum(fishing_hours, na.rm = T),
            total_fishing_KWh = sum(fishing_KWh, na.rm = T)) %>% 
  arrange(desc(total_vessels)) %>%
  ungroup() %>%
  mutate(vessel_rank = dense_rank(desc(total_vessels)),
         capacity_rank = dense_rank(desc(total_capacity)),
         fishing_hours_rank = dense_rank(desc(total_fishing_hours)),
         fishing_KWh_rank = dense_rank(desc(total_fishing_KWh))) %>%
  mutate(avg_rank = rowMeans(select(., c(vessel_rank, capacity_rank, fishing_hours_rank, fishing_KWh_rank))))

  # Save
  write_csv(EEZ_ranking, paste0(eez_results_dir, "EEZ_ranking_avg_", analysis_year, ".csv"))

}
```

Alternatively, we may want to run the EEZ analysis for all ACP countries.

```{r}
if(run_eez){
  
# Get codes/name to run anlysis for 
if(eez_purpose == "top_ranked"){
  
  EEZ_ranking_top <- EEZ_ranking %>%
    top_n(-number_of_top_countries_eez, wt = avg_rank)

  analysis_eezs <- EEZ_ranking_top$eez_code
  analysis_eez_territory_iso3 <- EEZ_ranking_top$eez_territory_iso3
  analysis_eez_territory_name <- countrycode(analysis_eez_territory_iso3, "iso3c", "country.name")
  
  ##EEZ combinations for the selected subset
  eez_combinations <- dw_effort_final_manual %>%
    dplyr::filter(eez_code %in% analysis_eezs) %>%
    group_by(eez_code = as.numeric(eez_code), eez_territory_iso3, flag) %>%
    summarize(vessels = n_distinct(ssvid),
              capacity = sum(engine_power_kw, na.rm = T),
              fishing_h = sum(fishing_hours_year_eez, na.rm = T),
              fishing_KWh = sum(fishing_KWh_year_eez, na.rm = T)) %>%
    arrange(eez_code) %>%
    ungroup() %>%
    mutate(region = "Africa")
  
  # Combine with coordinates
  eez_mapping <- eez_combinations %>%
    left_join(eez_map_centroid_coordinates, by = c("eez_code" = "eez_code", "region" = "region")) %>%
    left_join(land_eez_map_centroid_coordinates, by = c("flag" = "flag", "region" = "region")) 
  
   # There are some flag states for which we need to manually assign centroids: Hong Kong
   # Vessels with an unknown flag do not have lat/lon coordinates
  # Hong Kong (HKG)
  eez_mapping$flag_lon[eez_mapping$flag == "HKG" & eez_mapping$region == "Africa"] <- 22.409
  eez_mapping$flag_lat[eez_mapping$flag == "HKG" & eez_mapping$region == "Africa"] <- 114.139
  

}else if(eez_purpose == "ACP"){
  
  ACP_codes <- read_csv(here::here("SubsidyAtlasACP", "data", "ACP_eez_codes.csv")) %>% 
    dplyr::select(territory, territory_iso3, mrgid, region) %>%
    dplyr::filter(!is.na(mrgid))
  
  ACP_eez_filter <- EEZ_ranking %>%
    dplyr::filter(eez_code %in% ACP_codes$mrgid)
  
  analysis_eezs <- ACP_eez_filter$eez_code
  analysis_eez_territory_iso3 <- ACP_eez_filter$eez_territory_iso3
  analysis_eez_territory_name <- countrycode(analysis_eez_territory_iso3, "iso3c", "country.name")
  
  ##EEZ combinations for the selected subset
  eez_combinations <- dw_effort_final_manual %>%
    dplyr::filter(eez_code %in% analysis_eezs) %>%
    group_by(eez_code = as.numeric(eez_code), eez_territory_iso3, flag) %>%
    summarize(vessels = n_distinct(ssvid),
              capacity = sum(engine_power_kw, na.rm = T),
              fishing_h = sum(fishing_hours_year_eez, na.rm = T),
              fishing_KWh = sum(fishing_KWh_year_eez, na.rm = T)) %>%
    arrange(eez_code) %>%
    ungroup() %>%
    left_join(ACP_codes %>% dplyr::select(mrgid, region), by = c("eez_code" = "mrgid"))
  
  # Combine with coordinates
  eez_mapping <- eez_combinations %>%
    left_join(eez_map_centroid_coordinates, by = c("eez_code" = "eez_code", "region" = "region")) %>%
    left_join(land_eez_map_centroid_coordinates, by = c("flag" = "flag", "region" = "region")) 
  
  # The only flag states with NA flag_long/flag_lat coordiantes coorespond to vessels with an unknown flag so we're good there
}

}

```

In order to make our connection plots, we again need the centroids of each EEZ and flag state, which we match to each of our top EEZs, as well as to all flag states from which vessels are fishing in each EEZ.


```{r}
if(run_eez){

if(eez_purpose == "top_ranked"){  
# We then make our lines from each EEZ going to all of the countries fishing there. 
eez_mapping_wlines <- eez_mapping %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>%
  bind_cols(eez_mapping) %>%
  select(everything(), geometry) %>%
  st_segmentize(units::set_units(100,km)) %>%
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>%
  sf::st_sf(crs = 4326)

st_write(eez_mapping_wlines, dsn = paste0(eez_results_dir, "eez_mapping_with_lines.shp"),  delete_dsn=TRUE, driver = "ESRI Shapefile")

}else if(eez_purpose == "ACP"){

# Africa
eez_mapping_wlines_africa <- eez_mapping %>%
  dplyr::filter(!is.na(flag_lon)) %>%
  dplyr::filter(region == "Africa") %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(eez_mapping %>% dplyr::filter(!is.na(flag_lon)) %>% dplyr::filter(region == "Africa")) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326) 

 test_plot_africa <- ggplot()+
  geom_sf(data = eez_map, fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = land_eez_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = land_eez_map %>% dplyr::filter(iso3 %in% eez_mapping_wlines_africa$flag), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = eez_map %>% dplyr::filter(mrgid %in% eez_mapping_wlines_africa$eez_code), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = eez_mapping_wlines_africa, col = "darkgoldenrod", size = 0.25) +
  maptheme+
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

# Caribbean
eez_mapping_wlines_caribbean <- eez_mapping %>%
  dplyr::filter(flag != "UNK") %>%
  dplyr::filter(region == "Caribbean") %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(eez_mapping %>% dplyr::filter(flag != "UNK") %>% dplyr::filter(region == "Caribbean")) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>% 
  #mutate(geometry = (geometry + c(-100,90)) %% c(360) - c(260,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=100"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326) 

 test_plot_caribbean <- ggplot()+
  geom_sf(data = eez_map, fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = land_eez_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = land_eez_map %>% dplyr::filter(iso3 %in% eez_mapping_wlines_caribbean$flag), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = eez_map %>% dplyr::filter(mrgid %in% eez_mapping_wlines_caribbean$eez_code), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = eez_mapping_wlines_caribbean, col = "darkgoldenrod", size = 0.25) +
  maptheme+
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

eez_mapping_wlines_pacific <- eez_mapping %>%
  dplyr::filter(flag != "UNK") %>%
  dplyr::filter(region == "Pacific") %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(eez_mapping %>% dplyr::filter(flag != "UNK") %>% dplyr::filter(region == "Pacific")) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  mutate(geometry = (geometry + c(360,90)) %% c(360) - c(0,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=0"), quiet = TRUE) %>%
  sf::st_sf(crs = 4326) 

 test_plot_pacific <- ggplot()+
  geom_sf(data = eez_map, fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = land_eez_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = land_eez_map %>% dplyr::filter(iso3 %in% eez_mapping_wlines_pacific$flag), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = eez_map %>% dplyr::filter(mrgid %in% eez_mapping_wlines_pacific$eez_code), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = eez_mapping_wlines_pacific, col = "darkgoldenrod", size = 0.25) +
  maptheme+
  #coord_sf(xlim = c(0,360), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))


eez_mapping_wlines <- eez_mapping_wlines_africa %>%
  rbind(eez_mapping_wlines_caribbean) %>%
  rbind(eez_mapping_wlines_pacific)


st_write(eez_mapping_wlines, dsn = paste0(eez_results_dir, "eez_mapping_with_lines.shp"),  delete_dsn=TRUE, driver = "ESRI Shapefile")
st_write(eez_mapping_wlines, dsn = paste0(eez_results_app_dir, "eez_mapping_with_lines.shp"),  delete_dsn=TRUE, driver = "ESRI Shapefile")

}
}
```

We first need to make the connectivity maps... 

```{r}
if(run_eez){
  
  eez_loop_iso3 <- unique(analysis_eez_territory_iso3)
  eez_loop_names <- unique(analysis_eez_territory_name)

## For loop to run top EEZs
for(i in 61:length(eez_loop_iso3)){
  
run_eez_codes <- analysis_eezs[which(analysis_eez_territory_iso3 == eez_loop_iso3[i])]

eez_dat <- eez_mapping_wlines %>%
  dplyr::filter(eez_territory_iso3 == eez_loop_iso3[i]) 

# Make EEZ connection plot
eez_connectivity_map <- ggplot()+
  geom_sf(data = eez_map, fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = land_eez_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = land_eez_map %>% dplyr::filter(iso3 %in% eez_dat$flag), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = eez_map %>% dplyr::filter(mrgid %in% run_eez_codes), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = eez_dat, col = "darkgoldenrod", size = 0.25) +
  maptheme+
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

#plot_map pngs
ggsave(eez_connectivity_map, filename = paste0(eez_figures_dir, eez_loop_iso3[i], "_EEZ_connectivity_map.png"), width = 10, units = "in")

# Combine map into a one page pdf
title3 <- textGrob(paste0("Global network of distant-water fishing\nEEZ: ", eez_loop_names[i]), gp = gpar(fontsize=16, fontface="bold", lineheight=1, col = "white", fontfamily = "Helvetica"), hjust = 0.55, vjust = 1)

caption3 <- textGrob(paste0("This map shows the global origins of distant-water vessels fishing in the EEZ of", eez_loop_names[i], ". Lines connect the EEZ (blue) \nwith all foreign countries (pink) from which vessels fishing in that EEZ in 2018 are flagged. Data were taken from Global Fishing Watch (2018)."), gp = gpar(fontsize = 10, col = "white", fontfamily = "Helvetica"), vjust = 0, hjust = 0.5)

lay3 <- rbind(c(1,4),
              c(2,2),
              c(2,2),
              c(3,3))

# White SFG Logo
sfg_logo_white <- readPNG(here::here("common", "sfg-logo-white.png"))
logo_white <- rasterGrob(sfg_logo_white, interpolate=TRUE, vjust = 0.8, hjust = 0.6)

# Put together connectivity map
eez_page <- grid.arrange(title3, eez_connectivity_map, caption3, logo_white, 
                         layout_matrix = lay3,
                         heights=unit(c(1,1.5,5,1), c("in")), 
                         widths=unit(c(8.25,2.75), "in"))
out3 <- cowplot::ggdraw(eez_page) + 
  theme(plot.background = element_rect(fill="grey27", color = NA))

# Save connectivity map
ggsave(out3, filename = paste0(eez_pdf_dir, eez_loop_iso3[i], "_map_page.pdf"), width = 11, height = 8.5, units = "in")

### Step 2 - make heat maps
eezmaptheme <- theme_minimal()+
  theme(plot.background = element_rect(fill = "grey27", color = NA),
        panel.background = element_rect(fill = "grey27", color = NA),
        panel.grid.major = element_line(colour = "grey27"),
        text = element_text(color = "white"),
        plot.title = element_text(hjust = 0.5),
        panel.border = element_rect(color = "white", fill = NA),
        plot.margin = margin(t = 0, r = 0.1, b = 0, l = 0, unit = "cm"),
        legend.margin = margin(t = 0.1, r = 0, b = 0.1, l = 0, unit = "cm"),
        legend.position = "bottom",
        legend.box = "horizontal",
        axis.text = element_text(color = "white"))

# Pull data from GFW if necessary
 if(rerun_gfw == T){
   
    # What bin size do we want to use (degrees)?  
    bin_size <- 0.1
    
    # Voodoo to deal with some territories having multiple EEZs
    if(length(run_eez_codes) > 1){
      run_eez_codes_string <- toString(sprintf("'%s'", run_eez_codes))
      run_eez_text <- paste0("eez_code IN (", run_eez_codes_string, ")")
    }else {
      run_eez_codes_string <- run_eez_codes
      run_eez_text <- paste0("eez_code = '", run_eez_codes_string, "'")
      
    }
    
sql4 <- paste0(
  "WITH
  eez_lookup AS (
    SELECT
      CAST(eez_id AS string) eez_code,
      territory1_iso3 eez_territory_iso3
    FROM
      `world-fishing-827.gfw_research.eez_info`),

  selected_vi AS (
    SELECT
       year,
       ssvid,
       engine_power_kw,
       flag,
       eez_code
    FROM
       `ucsb-gfw.subsidy_atlas.FINAL_dw_effort_by_eez_", analysis_year, "`),
   
  eez_info AS (
     SELECT
       EXTRACT(year FROM _partitiontime) year,
       if(ARRAY_LENGTH(regions.eez)=0, '0000', regions.eez[ordinal(1)]) eez_code,
       ssvid,
       FLOOR(lat/", bin_size,") * ", bin_size, " + ", bin_size/2, " AS lat_cen,
       FLOOR(lon/", bin_size, ") * ", bin_size, " + ", bin_size/2, " AS lon_cen,
      CASE WHEN COUNT(DISTINCT _partitiontime) IS NULL THEN 0 ELSE COUNT(DISTINCT _partitiontime) END fishing_days,
      CASE WHEN SUM(hours) IS NULL THEN 0 ELSE SUM(hours) END fishing_hours
     FROM
       `world-fishing-827.gfw_research.pipe_production_b_fishing`
     WHERE
       nnet_score2 > .5
       AND seg_id IN (
          SELECT
            seg_id
          FROM
            `world-fishing-827.gfw_research.pipe_production_b_segs`
          WHERE
            good_seg)
    GROUP BY
      year,
      eez_code,
      ssvid,
      lat_cen,
      lon_cen
    HAVING
      year = ", analysis_year, 
      " AND ", run_eez_text, 
      " AND fishing_hours >= 1)
      
 SELECT
    a.year,
    a.eez_code,
    eez_territory_iso3,
    flag,
    lat_cen,
    lon_cen,
    SUM(a.fishing_hours) as fishing_hours,
    SUM(a.fishing_days) as fishing_days,
    SUM(a.fishing_hours * b.engine_power_kw) as fishing_KWh,
    SUM(a.fishing_hours * b.engine_power_kw * c.subs_per_fishing_KWh) as subs
  FROM
    eez_info a
  INNER JOIN 
    selected_vi b 
  ON 
    a.ssvid = b.ssvid AND 
    a.eez_code = b.eez_code
  LEFT JOIN
    `ucsb-gfw.subsidy_atlas.subsidy_rates_flag` c
  USING
    (flag)
  LEFT JOIN
    eez_lookup d
  ON
    a.eez_code = d.eez_code
  GROUP BY
    year,
    eez_code,
    eez_territory_iso3,
    flag,
    lat_cen,
    lon_cen
  ORDER BY
    flag"
  )

  eez_table <- bq_table(project = bq_project, table = paste0("fishing_effort_", eez_loop_iso3[i]), dataset = "subsidy_atlas") 

  if(bq_table_exists(eez_table) == FALSE){
    
    bq_table(project = bq_project, table = paste0("fishing_effort_", eez_loop_iso3[i]), dataset = "subsidy_atlas") %>%
      bq_table_create()
    
  }else{
    
    bq_table(project = bq_project, table = paste0("fishing_effort_", eez_loop_iso3[i]), dataset = "subsidy_atlas") %>%
      bq_table_delete()
    
  }

  eez_effort <- bq_project_query(bq_project, sql4, destination_table = bq_table(project = bq_project, table = paste0("fishing_effort_", eez_loop_iso3[i]), dataset = "subsidy_atlas"), use_legacy_sql = FALSE, allowLargeResults = TRUE) %>%
    bq_table_download(max_results = Inf)

  write_csv(eez_effort, path = paste0(eez_dat_dir, eez_loop_iso3[i], "_EEZ_effort_subs_by_flag.csv"))
  
  write_csv(eez_effort, path = paste0(eez_results_app_dir, eez_loop_iso3[i], "_EEZ_effort_subs_by_flag.csv"))

  # Load local data instead of rerunning global fishing watch pull 
  } else{
  
  eez_effort <- read_csv(paste0(eez_results_app_dir, eez_loop_iso3[i], "_EEZ_effort_subs_by_flag.csv"), col_types = "iccnnnnnnn")
    
  }

  ### Make Plots 
  # Get quantiles of data for scale limits
  eez_effort_aggregated <- eez_effort %>%
    group_by(year, eez_territory_iso3, lon_cen, lat_cen) %>%
    summarize(fishing_hours = sum(fishing_hours, na.rm = T),
              fishing_KWh = sum(fishing_KWh, na.rm = T),
              subs = sum(subs, na.rm = T)) %>%
    mutate(subsidy_intensity = subs/fishing_KWh)
  
    # Set map limits for filtering global country map and eez map appropriately
  x_lim <- c(min(eez_effort_aggregated$lon_cen) - 0.5, max(eez_effort_aggregated$lon_cen) + 0.5)
  y_lim <- c(min(eez_effort_aggregated$lat_cen) - 0.5, max(eez_effort_aggregated$lat_cen) + 0.5)
  
  # Quantiles
  if(length(unique(eez_effort_aggregated$subsidy_intensity)) <= 1){
    
  # Map of subsidy intensity
  eez_subsidy_plot <- ggplot()+
    geom_sf(data = land_eez_map, fill = "grey2", color = "grey40", size = 0.5)+ # world countries (dark grey, white border lines)
    geom_sf(data = eez_map, fill = NA, color = "grey60", size = 0.5)+ # world EEZs (transparent, light grey border lines)
    geom_raster(data = eez_effort_aggregated, aes(x = lon_cen, y = lat_cen, fill = subsidy_intensity))+
    eezmaptheme +
    scale_fill_viridis_c(na.value = NA, name = "Subsidy intensity \n(2018 $USD/KWh)", 
                         oob=scales::squish)+
    labs(x = "", y = "")+
    coord_sf(xlim = x_lim, ylim = y_lim)+
    guides(fill = guide_colorbar(title.position = "bottom", title.hjust = 0.5, barwidth = 18))+
    scale_x_continuous(expand = c(0,0))+
    scale_y_continuous(expand = c(0,0))
    
  }else{
    
    intensity_quantile <- quantile(eez_effort_aggregated$subsidy_intensity, probs = c(0.01, 0.05, 0.95, 0.99), na.rm = T)
  scale_labels <- round(seq(round(intensity_quantile[1], 1), round(intensity_quantile[4], 1), length.out = 5), 1)
  
   # Map of subsidy intensity
  eez_subsidy_plot <- ggplot()+
    geom_sf(data = land_eez_map, fill = "grey2", color = "grey40", size = 0.5)+ # world countries (dark grey, white border lines)
    geom_sf(data = eez_map, fill = NA, color = "grey60", size = 0.5)+ # world EEZs (transparent, light grey border lines)
    geom_raster(data = eez_effort_aggregated, aes(x = lon_cen, y = lat_cen, fill = subsidy_intensity))+
    eezmaptheme +
    scale_fill_viridis_c(na.value = NA, name = "Subsidy intensity \n(2018 $USD/KWh)", 
                         limits=c(round(intensity_quantile[1],1)-round(intensity_quantile[1],1)*0.01, round(intensity_quantile[4], 1) + round(intensity_quantile[4], 1)*0.01), 
                         labels=scale_labels,
                         breaks=scale_labels,
                         oob=scales::squish)+
    labs(x = "", y = "")+
    coord_sf(xlim = x_lim, ylim = y_lim)+
    guides(fill = guide_colorbar(title.position = "bottom", title.hjust = 0.5, barwidth = 18))+
    scale_x_continuous(expand = c(0,0))+
    scale_y_continuous(expand = c(0,0))
    
  }
  
  ggsave(eez_subsidy_plot, filename = paste0(eez_figures_dir, eez_loop_iso3[i], "_EEZ_subsidy_map.png"), width = 10, units = "in")
  
  # Labels for the log scale 
  eez_effort_plot <- ggplot()+
    geom_sf(data = land_eez_map, fill = "grey2", color = "grey40", size = 0.5)+ # world countries (dark grey, white border lines)
    geom_sf(data = eez_map, fill = NA, color = "grey60", size = 0.5)+ # world EEZs (transparent, light grey border lines)
    geom_raster(data = eez_effort_aggregated, aes(x = lon_cen, y = lat_cen, fill = fishing_KWh))+
    eezmaptheme +
    scale_fill_viridis_c(na.value = NA, option = "A", name = "Fishing effort \n(KWh)", trans = log10_trans(), labels = comma)+
    labs(x = "", y = "")+
    coord_sf(xlim = x_lim, ylim = y_lim) +
    guides(fill = guide_colorbar(title.position = "bottom", title.hjust = 0.5, barwidth = 18))+
    scale_x_continuous(expand = c(0,0))+
    scale_y_continuous(expand = c(0,0))
  
  ggsave(eez_effort_plot, filename = paste0(eez_figures_dir, eez_loop_iso3[i], "_EEZ_effort_map.png"), width = 10, units = "in")

  # Combined plot  
logo_white2 <- rasterGrob(sfg_logo_white, interpolate=TRUE, vjust = 0.8, hjust = 0.3)
  
title4 <- textGrob(paste0("Global network of distant-water fishing\nEEZ: ", eez_loop_names[i]), gp = gpar(fontsize=16, fontface="bold", lineheight=1, col = "white", fontfamily = "Helvetica"), hjust = 0.55, vjust = 1)

caption4 <- textGrob(paste0("These maps show distant-water fishing effort (left, KWh) and subsidy intensity (right, 2018 $USD/KWh) in the EEZ of ", eez_loop_names[i], ". \nBoth fishing effort and subsidy intensity are aggregated by 0.1 degree latitude/longitude. Data were taken from Global Fishing Watch (2018)."), gp = gpar(fontsize = 10, col = "white", fontfamily = "Helvetica"), vjust = 0, hjust = 0.5)

  if(eez_loop_iso3[i] == "RUS"){
    
    lay4 <- rbind(c(1,1,1,5),
              c(NA,NA,NA,NA),
              c(2,2,2,2),
              c(3,3,3,3),
              c(4,4,4,4))
    
    
  } else{
    
    lay4 <- rbind(c(1,1,1,5),
              c(NA,NA,NA,NA),
              c(2,2,3,3),
              c(2,2,3,3),
              c(4,4,4,4))
    
  }

# Put together connectivity map
page4 <- grid.arrange(title4, eez_effort_plot, eez_subsidy_plot, caption4, logo_white, 
                         layout_matrix = lay4,
                         heights=unit(c(1,0.5,3,3,1), c("in")),
                         widths=unit(c(2.75,2.75,2.75,2.75), "in"))
out4 <- cowplot::ggdraw(page4) + 
  theme(plot.background = element_rect(fill="grey27", color = NA))

# Save connectivity map
ggsave(out4, filename = paste0(eez_pdf_dir, eez_loop_iso3[i], "_effort_page.pdf"), width = 11, height = 8.5, units = "in")

# Save both plots into one pdf
  out_eez <- marrangeGrob(grobs = list(out3, out4), nrow = 1, ncol = 1, top = NULL)
  
  ggsave(out_eez, filename = paste0(eez_pdf_dir, eez_loop_iso3[i], "_combined.pdf"), width = 11, height = 8.5, units = "in")

}
}
```
