---
output:
  html_document: default

title: "Distant Water Fishing Atlas - Global Connectivity Analysis"
author: "Kat Millage, Matt Warham"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
---

# Introduction

This script uses our global list of distant water fishing vessels in 2018 to create the following summarized items: 
- Summary table showing total distant water fishing activity by EEZ/flag state 
- Connectivity lines for a given EEZ showing the origins of all distant water vessels

```{r setup, include=FALSE}
# Chunk options
knitr::opts_chunk$set(echo = TRUE)

### Load packages ------
library(sf) # spatial manipulation
library(lwgeom) # needed for curved lines
library(here) # path names
library(knitr) # knit document
library(countrycode) # country names 
library(tidyverse) # data manipulation
library(ggalt) # transform to robinson projection

# Path to vessel list
vessel_list_path <- here::here("results", "03b-distant-water-fishing", "vessel_list_2018_distant_water.csv")

# Path to eez file
eez_path <- here::here("data", "edited", "world_eez_v11_simple_neg360_360_ter_duplicates.gpkg")

# Path to land file
land_path <- here::here("data", "edited", "ne_50m_admin_neg360_360.gpkg")

### Create results directories
results_dir <- here::here("results/04b-connectivity-analysis/")
  if (dir.exists(results_dir) == F) { dir.create(results_dir, recursive = T) }

### Also save to app data directory
app_dir <- here::here("app-global/data/")
  if (dir.exists(app_dir) == F) { dir.create(app_dir, recursive = T) }
```

# Flag state / EEZ summaries

Since our vessel list of distant water fishing (and subsidies) is currently at the individual vessel level, we first want to aggregate this by flag state/eez. 

```{r}
# Load vessel list
vessel_list_raw <- read.csv(vessel_list_path, stringsAsFactors = F) 
```

```{r}
flag_eez_summary <- vessel_list_raw %>%
  group_by(eez_id, flag_iso3, is_EU) %>%
  summarize(n_vessels = n_distinct(ssvid),
            mean_length = mean(length_m, na.rm = T),
            mean_tonnage = mean(tonnage_gt, na.rm = T),
            mean_engine_power = mean(engine_power_kw),
            fishing_hours = sum(fishing_hours_eez_fao_ter, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T),
            ugly_subs = sum(ugly_subs, na.rm = T)) %>%
  ungroup() %>%
  arrange(flag_iso3, desc(eez_id))
```

Now let's load in our world and EEZ polygons so we can start matching them up and finding their centroids. 

```{r}
land_sf <- st_read(land_path) %>%
  st_set_crs(4326)

eez_sf <- st_read(eez_path) %>%
  st_set_crs(4326) %>%
  rename(eez_id = mrgid)
```

Starting with the EEZ file, let's attach our summary statistics directly to it to check that things match up. 

```{r}
# Match all rows (1442 obs)
eez_dw_sf <- eez_sf %>%
  full_join(flag_eez_summary, by = "eez_id")

# First extract rows with both a geoname and stats (1337 rows)
eez_dw_sf_match <- eez_dw_sf %>%
  dplyr::filter(!is.na(geoname) & !is.na(n_vessels))

# Let's find EEZs with no distant water fishing (97 entries)
# Most appear to belong to either EU states, 
eez_no_dw <- eez_dw_sf %>%
  dplyr::filter(is.na(n_vessels) & !is.na(geoname))

# Let's see if we have any outdated EEZ codes with distant water fishing, but no EEZ info (8 entries)
# Not ideal, but they all correspond to two EZZ codes: "8344" (Chagos Archipelago - UK/Mauritius) and "8399" (Bouvet Island - Norway). 
# Leaving these for now. 
eez_no_sf <- eez_dw_sf %>%
  dplyr::filter(!is.na(n_vessels) & is.na(geoname))

# Let's save all but the last category
eez_dw_sf <- eez_dw_sf %>%
  dplyr::filter((!is.na(n_vessels) & !is.na(geoname)) | (is.na(n_vessels) & !is.na(geoname)))
```

Now let's do something similar with our land file. 

```{r}
# Match all rows (1407 obs)
land_flag_sf <- land_sf %>%
  full_join(flag_eez_summary, by = c("admin_iso3" = "flag_iso3"))

# First extract rows with both an admin name and stats (1289 rows)
land_flag_sf_match <- land_flag_sf %>%
  dplyr::filter(!is.na(admin) & !is.na(n_vessels))

# Then find countries with no dw fishing vessels (112 rows)
land_no_dw <- land_flag_sf %>%
  dplyr::filter(!is.na(admin) & is.na(n_vessels))

# Any vessel flags with no matching land? (6 entries)
# All coorespond to "TUV" - "Tuvalu" doesn't appear on our map for some reason. Appears to only be one vessel, probably not a big deal. 
land_no_sf <- land_flag_sf %>%
  dplyr::filter(is.na(admin) & !is.na(n_vessels))

# Save all but the last
land_flag_sf <- land_flag_sf %>%
  dplyr::filter((!is.na(admin) & !is.na(n_vessels)) | (!is.na(admin) & is.na(n_vessels)))

```

# Connectivity plots

## EEZ Centroids 

In order to make our connection plots, we need to find the centroids of each EEZ and flag state so we can create the connectivity lines. In the Distant Water Fishing Atlas, this gets a little tricky because we want our plots to be centered on each EEZ of interest, depending on the region. 

This is why we have created files with our EEZ and country polygons duplicated and extended such that the total extent ranges from -360 to 360 degrees. We can then clip these to the appropriate extents for each of our seven regions, such that no polygons (and connectivity) lines should be getting bifurcated. 

For the purposes of plotting the EEZs in which the fishing activity is taking place, we're using a simplified form of the Maritime Boundaries - World EEZs (v11) from MarineRegions.org.

For our seven regions, we're using the following regional centroids: 
- East Asia & Pacific: (170, -5)
- Europe & Central Asia: (0, 50)
- Latin America & Caribbean: (-70, -15)
- Middle East & North Africa: (25, 10)
- North America: (-100, 40)
- South Asia: (80, 15)
- Sub-Saharan Africa: (25, -15) 

As a starting point, we'll therefore try creating our regional extents by going +/- 180 degrees from those points: 
- East Asia & Pacific: (-10, 350)
- Europe & Central Asia: (-180, 180)
- Latin America & Caribbean: (-250, -110)
- Middle East & North Africa: (-155, 205)
- North America: (-280, 80)
- South Asia: (-100, 260)
- Sub-Saharan Africa: (-155, 205) 

```{r}
map_coord <- list(east_asia_pacific = c(0, 360),
                  europe_central_asia = c(-180, 180),
                  latin_america_caribbean = c(-180, 180),
                  middle_east_north_africa = c(-180, 180),
                  north_america = c(-180, 180),
                  south_asia = c(-180, 180),
                  sub_saharan_africa = c(-180, 180))
```


```{r}
  # East Asia & Pacific
  east_asia_pacific_eez_sf <- st_crop(eez_sf, c(xmin = map_coord$east_asia_pacific[1],
                                                xmax = map_coord$east_asia_pacific[2],
                                                ymin=-90, ymax=90))
  east_asia_pacific_eez_centroids <- east_asia_pacific_eez_sf %>%
    st_centroid() %>%
    dplyr::select(eez_id, pol_type, geoname, eez_ter_iso3 = iso_ter, eez_ter_name = name_ter, eez_sov_iso3 = iso_sov, eez_sov_name = name_sov) %>%
    mutate(region = "East Asia & Pacific")
  
  # Europe & Central Asia
  europe_central_asia_eez_sf <- st_crop(eez_sf, c(xmin = map_coord$europe_central_asia[1],
                                                xmax = map_coord$europe_central_asia[2],
                                                ymin=-90, ymax=90))
  europe_central_asia_eez_centroids <- europe_central_asia_eez_sf %>%
    st_centroid() %>%
    dplyr::select(eez_id, pol_type, geoname, eez_ter_iso3 = iso_ter, eez_ter_name = name_ter, eez_sov_iso3 = iso_sov, eez_sov_name = name_sov) %>%
    mutate(region = "Europe & Central Asia")
  
  # Latin America & Caribbean
  latin_america_caribbean_eez_sf <- st_crop(eez_sf, c(xmin = map_coord$latin_america_caribbean[1],
                                                xmax = map_coord$latin_america_caribbean[2],
                                                ymin=-90, ymax=90))
  latin_america_caribbean_eez_centroids <- latin_america_caribbean_eez_sf %>%
    st_centroid() %>%
    dplyr::select(eez_id, pol_type, geoname, eez_ter_iso3 = iso_ter, eez_ter_name = name_ter, eez_sov_iso3 = iso_sov, eez_sov_name = name_sov) %>%
    mutate(region = "Latin America & Caribbean")
  
  # Middle East & North Africa
  middle_east_north_africa_eez_sf <- st_crop(eez_sf, c(xmin = map_coord$middle_east_north_africa[1],
                                                xmax = map_coord$middle_east_north_africa[2],
                                                ymin=-90, ymax=90))
  middle_east_north_africa_eez_centroids <- middle_east_north_africa_eez_sf %>%
    st_centroid() %>%
    dplyr::select(eez_id, pol_type, geoname, eez_ter_iso3 = iso_ter, eez_ter_name = name_ter, eez_sov_iso3 = iso_sov, eez_sov_name = name_sov) %>%
    mutate(region = "Middle East & North Africa")
  
  # North America
  north_america_eez_sf <- st_crop(eez_sf, c(xmin = map_coord$north_america[1],
                                                xmax = map_coord$north_america[2],
                                                ymin=-90, ymax=90))
  north_america_eez_centroids <- north_america_eez_sf %>%
    st_centroid() %>%
    dplyr::select(eez_id, pol_type, geoname, eez_ter_iso3 = iso_ter, eez_ter_name = name_ter, eez_sov_iso3 = iso_sov, eez_sov_name = name_sov) %>%
    mutate(region = "North America")
  
  # South Asia
  south_asia_eez_sf <- st_crop(eez_sf, c(xmin = map_coord$south_asia[1],
                                                xmax = map_coord$south_asia[2],
                                                ymin=-90, ymax=90))
  south_asia_eez_centroids <- south_asia_eez_sf %>%
    st_centroid() %>%
    dplyr::select(eez_id, pol_type, geoname, eez_ter_iso3 = iso_ter, eez_ter_name = name_ter, eez_sov_iso3 = iso_sov, eez_sov_name = name_sov) %>%
    mutate(region = "South Asia")
  
  # Sub Saharan Africa
  sub_saharan_africa_eez_sf <- st_crop(eez_sf, c(xmin = map_coord$sub_saharan_africa[1],
                                                xmax = map_coord$sub_saharan_africa[2],
                                                ymin=-90, ymax=90))
  sub_saharan_africa_eez_centroids <- sub_saharan_africa_eez_sf %>%
    st_centroid() %>%
    dplyr::select(eez_id, pol_type, geoname, eez_ter_iso3 = iso_ter, eez_ter_name = name_ter, eez_sov_iso3 = iso_sov, eez_sov_name = name_sov) %>%
    mutate(region = "Sub-Saharan Africa")
  
  # Bind together 
  eez_centroids <- east_asia_pacific_eez_centroids %>%
    rbind(europe_central_asia_eez_centroids) %>%
    rbind(latin_america_caribbean_eez_centroids) %>%
    rbind(middle_east_north_africa_eez_centroids) %>%
    rbind(north_america_eez_centroids) %>%
    rbind(south_asia_eez_centroids) %>%
    rbind(sub_saharan_africa_eez_centroids)
  
  # Put centroids in lon/lat columns
  eez_centroid_coordinates <- tibble(eez_id = eez_centroids$eez_id,
                                     pol_type = eez_centroids$pol_type,
                                     geoname = eez_centroids$geoname,
                                     eez_ter_iso3 = eez_centroids$eez_ter_iso3,
                                     eez_ter_name = eez_centroids$eez_ter_name,
                                     eez_sov_iso3 = eez_centroids$eez_sov_iso3,
                                     eez_sov_name = eez_centroids$eez_sov_name,
                                     region = eez_centroids$region) %>% 
    bind_cols(do.call(rbind, st_geometry(eez_centroids)) %>%
                as_tibble() %>%
                setNames(c("eez_lon", "eez_lat"))) %>%
    arrange(eez_id)
  
  # We only need one set of EEZ coordinates for each EEZ - let's figure out which region each EEZ is being displayed in. 
  eez_centroid_coordinates_keep <- eez_centroid_coordinates %>%
    mutate(region_to_keep = case_when(eez_ter_iso3 == "ATA" ~ "NA",
                                   eez_ter_iso3 == "ATF" ~ "Sub-Saharan Africa",
                                   eez_ter_iso3 == "ESH" ~ "Middle East & North Africa",
                                   eez_ter_iso3 == "MYT" ~ "Sub-Saharan Africa",
                                   eez_ter_iso3 == "REU" ~ "Sub-Saharan Africa",
                                   eez_ter_iso3 == "SHN" ~ "Sub-Saharan Africa",
                                   eez_ter_iso3 == "SJM" ~ "Europe & Central Asia",
                                   eez_ter_iso3 == "UMI" ~ "East Asia & Pacific",
                                   eez_ter_iso3 == "WLF" ~ "East Asia & Pacific",
                                   TRUE ~ countrycode(eez_ter_iso3, "iso3c", "region"))) %>%
    dplyr::filter(region == region_to_keep) %>%
    dplyr::select(-region_to_keep)
  
  write_csv(eez_centroid_coordinates_keep, paste0(results_dir, "eez_centroid_coordinates.csv"))
```

## Flag State Centroids 

We'll now repeat the process for our flag states. 

```{r}
  # East Asia & Pacific
  east_asia_pacific_land_sf <- st_crop(land_sf, c(xmin = map_coord$east_asia_pacific[1],
                                                xmax = map_coord$east_asia_pacific[2],
                                                ymin=-90, ymax=90))
  east_asia_pacific_land_centroids <- east_asia_pacific_land_sf %>%
    st_centroid() %>%
    dplyr::select(admin_iso3, admin, sov_iso3, sovereign, notes) %>%
    mutate(region = "East Asia & Pacific")
  
  # Europe & Central Asia
  europe_central_asia_land_sf <- st_crop(land_sf, c(xmin = map_coord$europe_central_asia[1],
                                                xmax = map_coord$europe_central_asia[2],
                                                ymin=-90, ymax=90))
  europe_central_asia_land_centroids <- europe_central_asia_land_sf %>%
    st_centroid() %>%
    dplyr::select(admin_iso3, admin, sov_iso3, sovereign, notes) %>%
    mutate(region = "Europe & Central Asia")
  
  # Latin America & Caribbean
  latin_america_caribbean_land_sf <- st_crop(land_sf, c(xmin = map_coord$latin_america_caribbean[1],
                                                xmax = map_coord$latin_america_caribbean[2],
                                                ymin=-90, ymax=90))
  latin_america_caribbean_land_centroids <- latin_america_caribbean_land_sf %>%
    st_centroid() %>%
    dplyr::select(admin_iso3, admin, sov_iso3, sovereign, notes) %>%
    mutate(region = "Latin America & Caribbean")
  
  # Middle East & North Africa
  middle_east_north_africa_land_sf <- st_crop(land_sf, c(xmin = map_coord$middle_east_north_africa[1],
                                                xmax = map_coord$middle_east_north_africa[2],
                                                ymin=-90, ymax=90))
  middle_east_north_africa_land_centroids <- middle_east_north_africa_land_sf %>%
    st_centroid() %>%
    dplyr::select(admin_iso3, admin, sov_iso3, sovereign, notes) %>%
    mutate(region = "Middle East & North Africa")
  
  # North America
  north_america_land_sf <- st_crop(land_sf, c(xmin = map_coord$north_america[1],
                                                xmax = map_coord$north_america[2],
                                                ymin=-90, ymax=90))
  north_america_land_centroids <- north_america_land_sf %>%
    st_centroid() %>%
    dplyr::select(admin_iso3, admin, sov_iso3, sovereign, notes) %>%
    mutate(region = "North America")
  
  # South Asia
  south_asia_land_sf <- st_crop(land_sf, c(xmin = map_coord$south_asia[1],
                                                xmax = map_coord$south_asia[2],
                                                ymin=-90, ymax=90))
  south_asia_land_centroids <- south_asia_land_sf %>%
    st_centroid() %>%
    dplyr::select(admin_iso3, admin, sov_iso3, sovereign, notes) %>%
    mutate(region = "South Asia")
  
  # Sub Saharan Africa
  sub_saharan_africa_land_sf <- st_crop(land_sf, c(xmin = map_coord$sub_saharan_africa[1],
                                                xmax = map_coord$sub_saharan_africa[2],
                                                ymin=-90, ymax=90))
  sub_saharan_africa_land_centroids <- sub_saharan_africa_land_sf %>%
    st_centroid() %>%
    dplyr::select(admin_iso3, admin, sov_iso3, sovereign, notes) %>%
    mutate(region = "Sub-Saharan Africa")
  
  # Bind together
  land_centroids <- east_asia_pacific_land_centroids %>%
    rbind(europe_central_asia_land_centroids) %>%
    rbind(latin_america_caribbean_land_centroids) %>%
    rbind(middle_east_north_africa_land_centroids) %>%
    rbind(north_america_land_centroids) %>%
    rbind(south_asia_land_centroids) %>%
    rbind(sub_saharan_africa_land_centroids)
  
  # Put centroids in lon/lat columns
  land_centroid_coordinates <- tibble(admin_iso3 = land_centroids$admin_iso3,
                                      admin = land_centroids$admin,
                                      sov_iso3 = land_centroids$sov_iso3,
                                      sovereign = land_centroids$sovereign,
                                      region = land_centroids$region) %>% 
    bind_cols(do.call(rbind, st_geometry(land_centroids)) %>%
                as_tibble() %>%
                setNames(c("flag_lon", "flag_lat"))) %>%
    arrange(admin_iso3) %>%
    na.omit() # removes Somaliland
  
  write_csv(land_centroid_coordinates, paste0(results_dir, "land_centroid_coordinates.csv"))

  
   # #Manually correct certain centroids
   # manual_coordinates_flags <- read_csv(paste0(results_dir, "corrected_flag_centroids.csv"))
   # 
   # land_eez_map_centroid_coordinates <- land_eez_map_centroid_coordinates %>%
   #   left_join(manual_coordinates_flags, by = c("flag", "region")) %>%
   #   mutate(flag_lon = ifelse(!is.na(flag_lon_edit), flag_lon_edit, flag_lon),
   #          flag_lat = ifelse(!is.na(flag_lat_edit), flag_lat_edit, flag_lat)) %>%
   #   dplyr::select(-flag_lon_edit, -flag_lat_edit)

```


## Add centroids to our EEZ/flag state distant water summary

```{r}
flag_eez_summary_centroids <- flag_eez_summary %>%
  left_join(eez_centroid_coordinates_keep, by = c("eez_id")) %>%
  left_join(land_centroid_coordinates, by = c("region", "flag_iso3" = "admin_iso3"))
```

### East Asia & Pacific

```{r}
# Let's do a test run with East Asia (-10, 350)
eez_mapping_wlines_east_asia_pacific <- flag_eez_summary_centroids %>%
  ungroup() %>%
  dplyr::filter(!is.na(flag_lon)) %>%
  dplyr::filter(region == "East Asia & Pacific") %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(flag_eez_summary_centroids %>% dplyr::filter(!is.na(flag_lon)) %>% dplyr::filter(region == "East Asia & Pacific")) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES", "DATELINEOFFSET=10"), quiet = TRUE) %>% 
  st_shift_longitude() %>%
  sf::st_sf(crs = 4326) 

test_dat_1 <- eez_mapping_wlines_east_asia_pacific %>%
  dplyr::filter(eez_id == 8455)

test_plot_east_asia_pacific <- ggplot()+
  geom_sf(data = eez_sf, fill = NA, color = "grey60", size = 0.1)+
  geom_sf(data = land_sf, fill = "grey2", color = "grey40", size = 0.1)+
  geom_sf(data = land_sf %>% dplyr::filter(admin_iso3 %in% test_dat_1$flag_iso3), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = eez_sf %>% dplyr::filter(eez_id %in% test_dat_1$eez_id), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = test_dat_1, col = "darkgoldenrod", size = 0.25) +
  coord_sf(xlim = c(-10,350), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

test_plot_east_asia_pacific
```
### All Others

```{r}
# Europe & Central Asia should be straightforward
eez_mapping_wlines_all_others <- flag_eez_summary_centroids %>%
  ungroup() %>%
  dplyr::filter(!is.na(flag_lon)) %>%
  dplyr::filter(region != "East Asia & Pacific") %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(flag_eez_summary_centroids %>% dplyr::filter(!is.na(flag_lon)) %>% dplyr::filter(region != "East Asia & Pacific")) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES", "DATELINEOFFSET=10"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326) 

test_dat_2 <- eez_mapping_wlines_all_others %>%
  dplyr::filter(eez_id == 8364)

test_plot_all_others <- ggplot()+
  geom_sf(data = eez_sf, fill = NA, color = "grey60", size = 0.1)+
  geom_sf(data = land_sf, fill = "grey2", color = "grey40", size = 0.1)+
  geom_sf(data = land_sf %>% dplyr::filter(admin_iso3 %in% test_dat_2$flag_iso3), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = eez_sf %>% dplyr::filter(eez_id %in% test_dat_2$eez_id), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = test_dat_2, col = "darkgoldenrod", size = 0.25) +
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

test_plot_all_others
```
```{r}
eez_mapping_wlines <- eez_mapping_wlines_east_asia_pacific %>%
  rbind(eez_mapping_wlines_all_others)

st_write(eez_mapping_wlines, paste0(results_dir, "eez_flag_state_connectivity_lines.gpkg"), delete_layer = T)
st_write(eez_mapping_wlines, paste0(app_dir, "eez_flag_state_connectivity_lines.gpkg"), delete_layer = T)
```





```{r}
# sql4 <- paste0(
#   "WITH
#   eez_lookup AS (
#     SELECT
#       CAST(eez_id AS string) eez_code,
#       territory1_iso3 eez_territory_iso3
#     FROM
#       `world-fishing-827.gfw_research.eez_info`),
# 
#   selected_vi AS (
#     SELECT
#        year,
#        ssvid,
#        engine_power_kw,
#        flag,
#        eez_code
#     FROM
#        `ucsb-gfw.subsidy_atlas.FINAL_dw_effort_by_eez_", analysis_year, "`),
#    
#   eez_info AS (
#      SELECT
#        EXTRACT(year FROM _partitiontime) year,
#        if(ARRAY_LENGTH(regions.eez)=0, '0000', regions.eez[ordinal(1)]) eez_code,
#        ssvid,
#        FLOOR(lat/", bin_size,") * ", bin_size, " + ", bin_size/2, " AS lat_cen,
#        FLOOR(lon/", bin_size, ") * ", bin_size, " + ", bin_size/2, " AS lon_cen,
#       CASE WHEN COUNT(DISTINCT _partitiontime) IS NULL THEN 0 ELSE COUNT(DISTINCT _partitiontime) END fishing_days,
#       CASE WHEN SUM(hours) IS NULL THEN 0 ELSE SUM(hours) END fishing_hours
#      FROM
#        `world-fishing-827.gfw_research.pipe_production_b_fishing`
#      WHERE
#        nnet_score2 > .5
#        AND seg_id IN (
#           SELECT
#             seg_id
#           FROM
#             `world-fishing-827.gfw_research.pipe_production_b_segs`
#           WHERE
#             good_seg)
#     GROUP BY
#       year,
#       eez_code,
#       ssvid,
#       lat_cen,
#       lon_cen
#     HAVING
#       year = ", analysis_year, 
#       " AND ", run_eez_text, 
#       " AND fishing_hours >= 1)
#       
#  SELECT
#     a.year,
#     a.eez_code,
#     eez_territory_iso3,
#     flag,
#     lat_cen,
#     lon_cen,
#     SUM(a.fishing_hours) as fishing_hours,
#     SUM(a.fishing_days) as fishing_days,
#     SUM(a.fishing_hours * b.engine_power_kw) as fishing_KWh,
#     SUM(a.fishing_hours * b.engine_power_kw * c.subs_per_fishing_KWh) as subs
#   FROM
#     eez_info a
#   INNER JOIN 
#     selected_vi b 
#   ON 
#     a.ssvid = b.ssvid AND 
#     a.eez_code = b.eez_code
#   LEFT JOIN
#     `ucsb-gfw.subsidy_atlas.subsidy_rates_flag` c
#   USING
#     (flag)
#   LEFT JOIN
#     eez_lookup d
#   ON
#     a.eez_code = d.eez_code
#   GROUP BY
#     year,
#     eez_code,
#     eez_territory_iso3,
#     flag,
#     lat_cen,
#     lon_cen
#   ORDER BY
#     flag"
#   )
# 
#   eez_table <- bq_table(project = bq_project, table = paste0("fishing_effort_", eez_loop_iso3[i]), dataset = "subsidy_atlas") 
# 
#   if(bq_table_exists(eez_table) == FALSE){
#     
#     bq_table(project = bq_project, table = paste0("fishing_effort_", eez_loop_iso3[i]), dataset = "subsidy_atlas") %>%
#       bq_table_create()
#     
#   }else{
#     
#     bq_table(project = bq_project, table = paste0("fishing_effort_", eez_loop_iso3[i]), dataset = "subsidy_atlas") %>%
#       bq_table_delete()
#     
#   }
#   
#    eez_effort <- bq_project_query(bq_project, sql4, destination_table = bq_table(project = bq_project, table = paste0("fishing_effort_", eez_loop_iso3[i]), dataset = "subsidy_atlas"), use_legacy_sql = FALSE, allowLargeResults = TRUE) %>%
#     bq_table_download(max_results = Inf)
# 
#   write_csv(eez_effort, path = paste0(eez_dat_dir, eez_loop_iso3[i], "_EEZ_effort_subs_by_flag.csv"))
#   
#   write_csv(eez_effort, path = paste0(eez_results_app_dir, eez_loop_iso3[i], "_EEZ_effort_subs_by_flag.csv"))
# 
#   # Load local data instead of rerunning global fishing watch pull 
#   } else{
#   
#   eez_effort <- read_csv(paste0(eez_results_app_dir, eez_loop_iso3[i], "_EEZ_effort_subs_by_flag.csv"), col_types = "iccnnnnnnn")
#     
#   }

```

 