---
output:
  html_document: default

title: "Atlas of distant water fishing - Analysis"
author: "Matthew Warham, Kat Millage"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
---

# Introduction

This script pulls information on fishing effort from Global Fishing Watch for distant water fishing vessels. The top countries with distant water fishing fleets and the top EEZs with the most distant water fishing activity are then identified.  


```{r setup, include=FALSE}
# Chunk options

knitr::opts_chunk$set(echo = TRUE)

# Packages
#library(maps)
library(sf) # spatial manipulation
library(lwgeom) # needed for curved lines
library(here) # path names
library(knitr) # knit document
library(bigrquery) # access GFW data
library(DBI) # access GFW data
library(countrycode) # country names 
library(tidyverse) # data manipulation
library(ggalt) # transform to robinson projection
library(RColorBrewer) # custom color palettes
library(scales) # scales for plotting
library(ggpubr) # plot arranging
library(gridExtra)
library(grid)
library(png)

# Set purpose of the flag state analysis ("top_ranked")
flag_state_purpose <- "top_ranked"
# Number of flag_states to include (if purpose is "top_ranked")
number_of_top_countries_flag <- 10

# Set purpose of the EEZ anlysis ("ACP" or "top_ranked")
eez_purpose <- "ACP"
# Number of EEZs to include (if purpose is "top_ranked")
number_of_top_countries_eez <- 10


# Set results directory
results_dir <- here::here("results/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

# Set directory for flag state results 
flag_state_results_dir <- paste0(results_dir, "flag_state_results/", flag_state_purpose, "/")
if (dir.exists(flag_state_results_dir) == F) {
  dir.create(flag_state_results_dir, recursive = T)
}

# Set directory for EEZ results
eez_results_dir <- paste0(results_dir, "eez_results/", eez_purpose, "/")
if (dir.exists(eez_results_dir) == F) {
  dir.create(eez_results_dir, recursive = T)
}

# If EEZ purpose is "ACP", also create a results directory for the app
if(eez_purpose == "ACP"){
    eez_results_app_dir <- paste0(here::here("SubsidyAtlasACP/"), "data/eez_results/", eez_purpose, "/")
    if (dir.exists(eez_results_app_dir) == F) {
      dir.create(eez_results_app_dir, recursive = T)
    }
}


# Connection to BigQuery
ucsb_project <-  "ucsb-gfw"
#gfw_project <- "world-fishing-827"

# Do you want to pull fresh data from GFW?
rerun_gfw <- T

# Choose analysis year (2012 - 2018)
analysis_year <- 2018
```

# Data pull from Global Fishing Watch

This section describes the process of linking to the most recent version of the GFW data, and pulling information on all distant water fishing vessels represented in that dataset. This process was last performed on 5/23/2019.  

We first extract total fishing hours (and fishing days) by year and EEZ for each vessel in the dataset. EEZs are defined by a numeric code, each cooresponding to a region in the World EEZ data set from Marineregions.org. The responsible territory for each region has been identified, as well as the sovereign country (or countries for disputed regions). We then match the best vessel characteristics identified by GFW to each vessel, and remove entries for all vessels that GFW does not consider to be fishing vessels. 

In order to separate entries cooresponding to distant water fishing effort, we remove all entries for vessels fishing on the high seas, and all vessel/EEZ pairings where the the flag state of the vessel is the same as the EEZ state or sovereign. We also remove all entries for vessels fishing less than one hour in a given EEZ in a year. 

```{r}
if(rerun_gfw == T){

# Query to pull fishing effort by vessel, by EEZ
sql <- "
WITH
  eez_lookup AS (
    SELECT
      CAST(eez_id AS string) eez_code,
      eez_type,
      reporting_name eez_name,
      territory1_iso3 eez_territory_iso3,
      sovereign1_iso3 eez_sovereign_iso3,
      sovereign2_iso3 eez_sovereign2_iso3,
      sovereign3_iso3 eez_sovereign3_iso3
    FROM
      `world-fishing-827.gfw_research.eez_info`),
      
 fishing_info_by_eez AS (
    SELECT
      EXTRACT(year FROM _partitiontime) year,
      ssvid,
      if(ARRAY_LENGTH(regions.eez)=0, '0000', regions.eez[ordinal(1)]) eez_code,
      CASE WHEN COUNT(DISTINCT _partitiontime) IS NULL THEN 0 ELSE COUNT(DISTINCT _partitiontime) END fishing_days_year_eez,
      CASE WHEN SUM(hours) IS NULL THEN 0 ELSE SUM(hours) END fishing_hours_year_eez
    FROM
      `world-fishing-827.gfw_research.pipe_production_b_fishing`
    WHERE
      nnet_score2 > .5
      AND seg_id IN (
        SELECT
          seg_id
            FROM
              `world-fishing-827.gfw_research.pipe_production_b_segs`
            WHERE
              good_seg)
    GROUP BY
      year,
      ssvid,
      eez_code)
 
SELECT
  year,
  ssvid,
  best.best_flag flag,
  best.best_vessel_class vessel_class,
  best.best_length_m length_m,
  best.best_tonnage_gt tonnage_gt,
  best.best_engine_power_kw engine_power_kw,
  ais_identity.shipname_mostcommon.value broadcast_shipname,
  ais_identity.n_callsign_mostcommon.value broadcast_callsign,
  eez_code,
  eez_type,
  eez_name,
  if(eez_territory_iso3 IS NULL, 'High Seas', eez_territory_iso3) eez_territory_iso3,
  eez_sovereign_iso3,
  eez_sovereign2_iso3,
  eez_sovereign3_iso3,
  fishing_hours_year_eez,
  fishing_days_year_eez
FROM
  fishing_info_by_eez
RIGHT JOIN
  `world-fishing-827.gfw_research.vi_ssvid_byyear_v20190430`
USING
  (year,
   ssvid)
LEFT JOIN
    eez_lookup
USING
    (eez_code)
WHERE 
  on_fishing_list_best
  AND activity.offsetting IS FALSE
ORDER BY
  year,
  eez_territory_iso3,
  eez_code,
  fishing_hours_year_eez DESC,
  ssvid"

# Store in bigquery - all_fishing_effort_by_eez (~700,000 rows - over 100MB)
bq_table(project = ucsb_project, table = "all_fishing_effort_by_eez", dataset = "subsidy_atlas") %>% 
  bq_table_delete()
bq_project_query(ucsb_project, sql, destination_table = bq_table(project = ucsb_project, table = "all_fishing_effort_by_eez",dataset = "subsidy_atlas"), use_legacy_sql = FALSE, allowLargeResults = TRUE)

# Let's exclude all entries where a vessel had less than 1 fishing hour in any eez in a given year, entries from the high seas, and entries where the flag of the vessel is the same as the administering territory of that eez
sql2 <- "
SELECT
  *
FROM
  `ucsb-gfw.subsidy_atlas.all_fishing_effort_by_eez`
WHERE 
fishing_hours_year_eez > 1 
and eez_territory_iso3 != 'High Seas'
and flag != eez_territory_iso3"

# Store in bigquery - all_dw_fishing_effort_by_eez (~100,000 rows - ~25MB)
bq_table(project = ucsb_project, table = "all_dw_fishing_effort_by_eez", dataset = "subsidy_atlas") %>% 
  bq_table_delete()

# Download results
all_dw_fishing_effort_by_eez <- bq_project_query(ucsb_project, sql2, destination_table = bq_table(project = ucsb_project, table = "all_dw_fishing_effort_by_eez", dataset = "subsidy_atlas"), use_legacy_sql = FALSE, allowLargeResults = TRUE) %>%
  bq_table_download(max_results = Inf)

# Make fishing_KWh and fishing_KW_day variables
dw_effort_raw <- all_dw_fishing_effort_by_eez %>%
  mutate(fishing_KWh = fishing_hours_year_eez*engine_power_kw,
         fishing_KW_days = fishing_days_year_eez*engine_power_kw)
dw_effort_raw[dw_effort_raw == "NA"] <- NA

# Fix a couple of iso3 codes that are outdated
dw_effort_raw$flag[dw_effort_raw$flag == "ROM"] <- "ROU"
dw_effort_raw$flag[dw_effort_raw$flag == "GCA"] <- "GTM"
dw_effort_raw$flag[is.na(dw_effort_raw$flag)] <- "UNK"

# Save file
write_csv(dw_effort_raw, path = paste0(results_dir, "RAW_dw_effort_by_eez.csv"))

} else{
  
# Pull local stored copy of the data 
dw_effort_raw <- read_csv(paste0(results_dir, "RAW_dw_effort_by_eez.csv"), col_types = "icccnnncccccccccninn")

#MW Pull local
#dw_effort <- read_csv("~/GitHub/subsidy-atlas/results/RAW_dw_effort_by_eez.csv")

}
```

# Determine the sovereign states of each flag state

GFW has done a lot of this work for us, therefore we use the sovereign states assigned to each eez iso3 for flag states as well. Let's find those.

```{r}
# Get a list of sovereignty pairings from GFW eez data
sovereign_pairings <- dw_effort_raw %>%
  distinct(eez_sovereign_iso3, eez_territory_iso3) %>%
  rename(sovereign_iso3 = eez_sovereign_iso3, iso3 = eez_territory_iso3) %>%
  na.omit() %>% # there's one entry where flag = CHN, and sovereign = NA
  arrange(iso3)

# Custom sovereignty pairings that are missing
c_sovereign_pairings <- tibble(iso3 = c("BLZ", "ARM", "AUT", "SRB", "CHE", "LIE", "UNK", "SVK", "MNG", "IRQ", "JOR", "HKG", "NER", "BOL", "LSO", "HUN", "KHM", "AFG")) %>%
  mutate(name = case_when(iso3 == "UNK" ~ "Unknown",
                          iso3 != "UNK" ~ countrycode::countrycode(iso3, "iso3c", "country.name")),
         sovereign_iso3 = case_when(iso3 == "HKG" ~ "CHN",
                                    TRUE ~ iso3))

# Put them all back together
sovereign_pairings_all <- sovereign_pairings %>%
  bind_rows(c_sovereign_pairings %>% dplyr::select(sovereign_iso3, iso3)) %>%
  arrange(iso3)
```

We then assign these names to the flag states of vessels, as well as to the EEZ states and sovereigns in the GFW database by matching ISO-3 character codes of each entity. 

```{r}
# Add sovereign state to each vessel in GFW
dw_effort <- dw_effort_raw %>%
  left_join(sovereign_pairings_all, by = c("flag" = "iso3"))

# Add names 
dw_effort <- dw_effort %>%
  mutate(flag_name = case_when(flag == "UNK" ~ "Unknown",
                               flag != "UNK" ~ countrycode::countrycode(flag, "iso3c", "country.name")),
         sovereign_name = case_when(sovereign_iso3 == "UNK" ~ "Unknown",
                               sovereign_iso3 != "UNK" ~ countrycode::countrycode(sovereign_iso3, "iso3c", "country.name")),
         eez_territory_name = case_when(eez_territory_iso3 == "ASC" | eez_territory_iso3 == "TAA" ~ countrycode::countrycode("SHN", "iso3c", "country.name"),
                                        eez_territory_iso3 == "CPT" ~ "Clipperton Island",
                                        TRUE ~ countrycode::countrycode(eez_territory_iso3, "iso3c", "country.name")),
         eez_sovereign_name = countrycode::countrycode(eez_sovereign_iso3, "iso3c", "country.name"),
         eez_sovereign2_name = countrycode::countrycode(eez_sovereign2_iso3, "iso3c", "country.name"),
         eez_sovereign3_name = countrycode::countrycode(eez_sovereign3_iso3, "iso3c", "country.name"))

```

# European Union vessels

Vessels flagged to EU member states have the right to fish in the EEZs of other EU member states, therefore we do not include these instances as "distant water fishing". In order to remove these from our dataset, we first need create a list of EU member states, as well as non-member states with with the EU has fishing agreements as part of the northern agreement (i.e. Norway and Iceland). 

We define "intra-EU fishing" as fishing activity that meets one of the following criteria: 
1. The flag state of the vessel is a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland and the EEZ in which it is fishing is administered by a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland (e.g. a French-flagged vessel fishing in the EEZ of Spain);
2. The sovereign of the vessel's flag state is a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland and the EEZ in which it is fishing is administered by a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland (e.g. a XXX-flagged vessel fishing in the EEZ of Spain).

We do not consider the following to be "intra-EU fishing": 
1. The flag state of the vessel is a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland and the EEZ in which it is fishing belongs to a territory or distant region of an EU member state (e.g. a French-flagged vessel fishing in the EEZ of French Polynesia). 

```{r}
# EU member states
# Austria, Belgium, Bulgaria, Croatia, Cyprus, Czechia, Denmark, Estonia, Finland, France, Germany, Greece, Hungary, Ireland, Italy, Latvia, Lithuania, Luxembourg, Malta, Netherlands, Poland, Portugal, Romania, Slovakia, Slovenia, Spain, Sweden, United Kingdom
eu_states <- c("AUT", "BEL", "BGR", "HRV", "CYP", "CZE", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "HUN", "IRL", "ITA", "LVA", "LTU", "LUX", "MLT", "NLD", "POL", "PRT", "ROU", "SVK", "SVN", "ESP", "SWE", "GBR")

# EU remote regions
# Wallis and Futuna, French Guiana, Sint Maarten (Dutch part), Saint Pierre and Miquelon, Saint Martin (French part), Mayotte, Saint Barthelemy, Reunion, Curaçao, Aruba, British Indian Ocean Territory, Bonaire, Saint Eustatius and Saba, Guadeloupe, Martinique, Saint Helena, Ascension and Tristan da Cunha, Ascension Island, South Georgia and the South Sandwich Islands, French Southern Territories, Tristan da Cunha, Falkland Islands (Malvinas), Bermuda, Turks and Caicos Islands, Cayman Islands, Virgin Islands, British, Anguilla, Montserrat, Pitcairn, French Polynesia
# eu_distant_states <- c('WLF', 'GUF', 'SXM', 'SPM', 'MAF', 'MYT', 'BLM', 'REU', 'CUW', 'ABW', 'IOT', 'BES', 'GLP', 'MTQ', 'SHN', 'ASC', 'SGS', 'ATF', 'TAA', 'FLK', 'BMU', 'TCA','CYM', 'VGB','AIA', 'MSR', 'PCN', 'PYF')

# States with which the EU has free fishing agreements 
# Norway, Svalbard and Jan Mayen, Iceland
eu_northern_agreement <- c("NOR", "SJM", "ISL")

# Identify flag/eez pairings which we're excluding from "distant water" because of the EU relationship between nations
dw_effort <- dw_effort %>%
  mutate(is_EU = ifelse(flag %in% c(eu_states, eu_northern_agreement) & eez_territory_iso3 %in% c(eu_states, eu_northern_agreement) |
                      sovereign_iso3 %in% c(eu_states, eu_northern_agreement) & eez_territory_iso3 %in% c(eu_states, eu_northern_agreement), 
                      TRUE, 
                      FALSE)) %>%
  dplyr::filter(!is_EU)

```
 
# Dealing with sovereignty

If the sovereign flag state of a vessel is the same as the sovereign state of the EEZ in which it's fishing, this connection may still be considered to be distant water fishing (e.g. US vessel fishing in Palmyra Atoll), though this is generally not considered to be foreign distant water fishing. Let's add a field identifying effort in which this is the case. Though we aren't making any distinctions between foreign distant water fishing and distant water fishing right now, it might be helpful later on to have this distinction available. 

We descibe "sovereign fishing" as fishing activity that meets one of the following criteria: 
1. The flag state of the vessel is the same as the sovereign of the administering territory of the EEZ in which it is fishing (e.g. a US flagged vessel fishing in the EEZ of Palmyra Atoll).
2. The sovereign of the flag state of the vessel is the same as the sovereign of the administering territory of the EEZ in which it is fishing (e.g. a Puerto-Rican flagged vessel fishing in the EEZ of Palmyra Atoll);


```{r}
# 4,922 connections are not foreign
dw_effort <- dw_effort %>%
  mutate(is_foreign = case_when(flag == eez_sovereign_iso3 | 
                                    flag == eez_sovereign2_iso3 | 
                                    flag == eez_sovereign3_iso3 |
                                    sovereign_iso3 == eez_sovereign_iso3 | 
                                    sovereign_iso3 == eez_sovereign2_iso3 |
                                    sovereign_iso3 == eez_sovereign3_iso3 ~ FALSE,
                                  TRUE ~ TRUE))
```

There are some cases in which there may be connections that are not foreign and that because of their particular situation should not be considered distant water. An example of this are disputed and joint regime EEZ.  These are listed and removed here:

```{r}
sovereign_connections <- dw_effort %>%
  filter(!is_foreign) %>%
  distinct(flag_name, sovereign_name, eez_code, eez_name, eez_type, eez_territory_name , eez_sovereign_name, eez_sovereign2_name, eez_sovereign3_name) %>%
  arrange(desc(sovereign_name))

non_distant_water_connections <- sovereign_connections %>%
  filter(!(flag_name == "United States" & eez_code %in% c("8442", "8443", "8444", "8451", "8452", "33179", "33180", "48980"))) %>%
  filter(!(flag_name == "Falkland Islands" & eez_territory_name == "St. Helena")) %>%
  filter(!(sovereign_name == "United Kingdom" & eez_territory_name == "South Georgia & South Sandwich Islands")) %>%
  filter(!(sovereign_name == "United Kingdom" & eez_territory_name == "Falkland Islands")) %>%
  filter(!(flag_name == "United Kingdom" & eez_territory_name == "Montserrat")) %>%
  filter(!(sovereign_name == "New Zealand")) %>%
  filter(!(sovereign_name == "France")) %>%
  filter(!(sovereign_name == "Australia" & eez_type == "200NM"))

dw_effort <- dw_effort %>%
  anti_join(non_distant_water_connections)

```

# Distant water fishing

For the purposes of this analysis, we define distant water fishing in the following way. We exclude all "intra-EU fishing", but include "sovereign fishing". All DW fishing that is not "sovereign fishing" is foreign DW fishing. 

```{r}
write_csv(dw_effort, paste0(results_dir, "FINAL_dw_effort_by_eez.csv"))

dw_effort_final <- dw_effort %>%
  dplyr::filter(year == analysis_year)

write_csv(dw_effort_final, paste0(results_dir, "FINAL_dw_effort_by_eez_", analysis_year, ".csv"))

```


# Assign subsidies
```{r}
# Now we need to get subsidy rates per fishing KWh for our DW vessels
# Since Rashid has not provided a DW and/or large-scale breakdown of his subsidy estimates, we need to figure out how to do this.
subsidy_dat <- read_csv(here::here("data", "subsidies", "Subsidies_update_Pew_final_May_10.csv")) %>%
  setNames(tolower(names(.))) %>%
  rename(value = `constant 2018 usd`,
         estimate_type = `data type`) %>%
  mutate(iso3 = countrycode(country, "country.name", 'iso3c'))
subsidy_dat$iso3[subsidy_dat$country == "Dominican Rp"] <- "DOM"
subsidy_dat$iso3[subsidy_dat$country == "Micronesia"] <- "FSM"
subsidy_dat$iso3[subsidy_dat$country == "Untd Arab Em"] <- "ARE"

# Order factors for custom color scale
subsidy_dat_factors <- subsidy_dat %>%
  distinct(category, type)

category_factor_order <- c(unique(subsidy_dat_factors$category))
type_factor_order <- c(subsidy_dat_factors$type)

subsidy_dat_ordered <- subsidy_dat %>%
  mutate(type = factor(type, levels = type_factor_order, ordered = T),
         category = factor(category, levels = category_factor_order, ordered = T))

  # Get sums of subsidy data by category for each country
subsidy_dat_summarized <- subsidy_dat_ordered %>%
  group_by(iso3, category) %>%
  summarize(value = sum(value, na.rm = T))

# Calculate effort totals by flag and then subsidy rates
dw_subsidy_rates_flag <- dw_effort_final %>%
  group_by(flag) %>%
  summarize(fishing_hours = sum(fishing_hours_year_eez, na.rm = T),
            fishing_days = sum(fishing_days_year_eez, na.rm = T),
            fishing_KWh = sum(fishing_KWh, na.rm = T),
            fishing_KW_days = sum(fishing_KW_days, na.rm = T)) %>%
  left_join(subsidy_dat_summarized %>% dplyr::filter(category == "Capacity-enhancing"), by = c("flag" = "iso3")) %>%
  mutate(subs_per_fishing_hour = value/fishing_hours,
         subs_per_fishing_day = value/fishing_days,
         subs_per_fishing_KWh = value/fishing_KWh,
         subs_per_fishing_KW_day = value/fishing_KW_days)
dw_subsidy_rates_flag$category[is.na(dw_subsidy_rates_flag$category)] <- "Capacity-enhancing"
dw_subsidy_rates_flag$value[is.na(dw_subsidy_rates_flag$value)] <- 0
dw_subsidy_rates_flag$subs_per_fishing_hour[is.na(dw_subsidy_rates_flag$subs_per_fishing_hour)] <- 0
dw_subsidy_rates_flag$subs_per_fishing_KWh[is.na(dw_subsidy_rates_flag$subs_per_fishing_KWh)] <- 0
dw_subsidy_rates_flag$subs_per_fishing_day[is.na(dw_subsidy_rates_flag$subs_per_fishing_day)] <- 0
dw_subsidy_rates_flag$subs_per_fishing_KW_day[is.na(dw_subsidy_rates_flag$subs_per_fishing_KW_day)] <- 0

```

# Identify top DW fishing fleets by flag state

We identify the top `r number_of_top_countries_flag` flag states with DW fishing fleets. We consider the following metrics:
- Number of fishing vessels partaking in DW fishing
- Total capacity of fishing vessels partaking of DW fishing
- Total number of DW fishing hours
- Total number of DW fishing KWh 

```{r cars}
# Mutate totals by flag state
flag_state_ranking <- dw_effort_final %>% 
  group_by(flag, ssvid) %>%
  summarize(engine_power_kw = unique(engine_power_kw),
            fishing_hours = sum(fishing_hours_year_eez, na.rm = T),
            fishing_KWh = sum(fishing_KWh, na.rm = T)) %>%
  ungroup() %>%
  group_by(flag) %>%
  summarize(total_vessels = n_distinct(ssvid),
            total_capacity = sum(engine_power_kw, na.rm = T),
            total_fishing_hours = sum(fishing_hours, na.rm = T),
            total_fishing_KWh = sum(fishing_KWh, na.rm = T)) %>% 
  arrange(desc(total_vessels)) %>%
  ungroup() %>%
  mutate(vessel_rank = dense_rank(desc(total_vessels)),
         capacity_rank = dense_rank(desc(total_capacity)),
         fishing_hours_rank = dense_rank(desc(total_fishing_hours)),
         fishing_KWh_rank = dense_rank(desc(total_fishing_KWh))) %>%
  mutate(avg_rank = rowMeans(select(., c(vessel_rank, capacity_rank, fishing_hours_rank, fishing_KWh_rank))))

# flag_state_combinations_ranking <- dw_effort_final %>%
#   distinct(flag, eez_code = as.numeric(eez_code)) %>%
#   arrange(flag) %>%
#   group_by(flag) %>%
#   summarize(num_eezs = n_distinct(eez_code)) %>%
#   mutate(eez_rank = dense_rank(desc(num_eezs))) %>%
#   arrange(eez_rank)

# Identify top flag states based on average ranking
flag_state_ranking_top <- flag_state_ranking %>%
 top_n(-number_of_top_countries_flag, wt = avg_rank)

# Output tables 
# create tables directory
flag_table_dir <- paste0(flag_state_results_dir, "tables/")
if (dir.exists(flag_table_dir) == F) {
  dir.create(flag_table_dir, recursive = T)
}

write_csv(flag_state_ranking_top, paste0(flag_table_dir, "top_", number_of_top_countries_flag, "_flag_states_avg_", analysis_year, ".csv"))

# Just in case - let's make top lists for each category as well
# Vessels
write_csv(flag_state_ranking %>%
            top_n(-number_of_top_countries_flag, wt = vessel_rank), 
          paste0(flag_table_dir, "top_", number_of_top_countries_flag, "_flag_states_vessels_", analysis_year, ".csv"))

# Total capacity
write_csv(flag_state_ranking %>%
            top_n(-number_of_top_countries_flag, wt = capacity_rank), 
          paste0(flag_table_dir, "top_", number_of_top_countries_flag, "_flag_states_capacity_", analysis_year, ".csv"))

# Fishing hours
write_csv(flag_state_ranking %>%
            top_n(-number_of_top_countries_flag, wt = fishing_hours_rank), 
          paste0(flag_table_dir, "top_", number_of_top_countries_flag, "_flag_states_fishing_hours_", analysis_year, ".csv"))

# Fishing KWh
write_csv(flag_state_ranking %>%
            top_n(-number_of_top_countries_flag, wt = fishing_KWh_rank), 
          paste0(flag_table_dir, "top_", number_of_top_countries_flag, "_flag_states_fishing_KWh_", analysis_year, ".csv"))

```

For each of our top flag states, we identify all EEZs in which DW vessels flagged to that state fish. 

```{r}
top_flag_states <- flag_state_ranking_top$flag

top_flag_states_names <- (tibble(flag = top_flag_states) %>%
  mutate(name = countrycode::countrycode(flag, "iso3c", "country.name")))$name

flag_state_combinations <- dw_effort_final %>%
  dplyr::filter(flag %in% top_flag_states) %>%
  group_by(flag, eez_code = as.numeric(eez_code)) %>%
  summarize(vessels = n_distinct(ssvid),
            capacity = sum(engine_power_kw, na.rm = T),
            fishing_h = sum(fishing_hours_year_eez, na.rm = T),
            fishing_KWh = sum(fishing_KWh, na.rm = T)) %>%
  arrange(flag) %>%
  ungroup()
```

In order to make our connection plots, we find the centroids of each EEZ and flag state. 

```{r}
### EEZs -----
# Get centroids of each eez
EEZ_map <- read_sf(dsn = here::here("data", "shapefiles", "eez_v10_fao_combined_simple"), layer = "eez_v10_fao_combined_simple") %>% 
  st_transform(crs = 4326)

EEZ_map_centroids <- EEZ_map %>%
  dplyr::filter(is.na(zone)) %>%
  st_centroid() %>%
  dplyr::select(eez_code = mrgid, eez_name = geoname, geometry)

centroid_coordinates_EEZ <- tibble(eez_code = EEZ_map_centroids$eez_code,
                                   eez_name = EEZ_map_centroids$eez_name) %>% 
  bind_cols(do.call(rbind, st_geometry(EEZ_map_centroids)) %>% 
    as_tibble() %>% setNames(c("eez_lon","eez_lat"))) %>%
  arrange(eez_code)

manual_coordinates_EEZ <- read_csv(paste0(results_dir, "corrected_EEZ_centroids.csv"))

#MW load
#manual_coordinates_EEZ <- read_csv("~/GitHub/subsidy-atlas/results/corrected_EEZ_centroids.csv")

centroid_coordinates_EEZ_edited <- centroid_coordinates_EEZ %>% 
  left_join(manual_coordinates_EEZ, by = c("eez_code")) %>% 
  mutate(eez_lon = ifelse(!is.na(eez_lon_edit), eez_lon_edit, eez_lon)) %>% 
  mutate(eez_lat = ifelse(!is.na(eez_lat_edit), eez_lat_edit, eez_lat)) %>%
  dplyr::select(-eez, -eez_lat_edit, -eez_lon_edit)

### Flag states -----
# Get centroids of each flag state
country_map <- read_sf(dsn = here::here("data", "shapefiles", "world_happy_180"), layer = "world_happy_180") %>%  
  st_transform(crs = 4326)

country_map_centroids <- country_map %>%
  st_centroid() %>%
  dplyr::select(iso3, geometry)

centroid_coordinates_flag <- tibble(flag = country_map$iso3) %>% 
  bind_cols(do.call(rbind, st_geometry(country_map_centroids)) %>% 
    as_tibble() %>% setNames(c("flag_lon","flag_lat"))) %>%
  arrange(flag)

manual_coordinates_flags <- read_csv(paste0(results_dir, "corrected_flag_centroids.csv"))

#MW Load
#manual_coordinates_flags <- read_csv("~/GitHub/subsidy-atlas/results/corrected_flag_centroids.csv")

centroid_coordinates_flag_edited <- centroid_coordinates_flag %>% 
  left_join(manual_coordinates_flags, by = c("flag")) %>% 
  mutate(flag_lon = ifelse(!is.na(flag_lon_edit), flag_lon_edit, flag_lon)) %>% 
  mutate(flag_lat = ifelse(!is.na(flag_lat_edit), flag_lat_edit, flag_lat)) %>%
  dplyr::select(-flag_lon_edit, -flag_lat_edit)

```

```{r}
### Simple Pacific centered EEZ's

library(sf)
library(rmapshaper)

pacific_shapefile <- read_sf(dsn = here::here("data", "shapefiles", "World_EEZ_v9_20161021_HR_0_360"), layer = "World_EEZ_v9_2016_HR_0_360") %>%
  ms_simplify() #%>% 
  #st_transform(crs = 4326)
    #dplyr::select(assessid, shp_source, geometry)



leaflet() %>% 
      addProviderTiles("CartoDB.DarkMatterNoLabels") %>% 
      addPolygons(data = pacific_lowres, 
                  fillColor = "slateblue",
                  fillOpacity = 0.8,
                  color= "white",
                  weight = 0.3,
                  highlight = highlightOptions(weight = 5,
                                               color = "#666",
                                               fillOpacity = 1,
                                               bringToFront = TRUE),
                  label = ("Africa"))


```


We then match these centroids to each of our top flag states, as well as all EEZs in which DW vessels from these states fish. 

```{r}
flag_state_mapping <- flag_state_combinations %>%
  left_join(centroid_coordinates_flag_edited, by = c("flag" = "flag")) %>%
  left_join(centroid_coordinates_EEZ_edited, by = c("eez_code" = "eez_code"))
  
flag_state_mapping_wlines <- flag_state_mapping %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(flag_state_mapping) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326)
```

```{r flagmaps}
# Custom theme for map
maptheme <- theme_minimal()+
  theme(panel.background = element_rect(fill = "grey27", colour = NA),
        panel.grid.major = element_line(colour = "grey27"),
        panel.border = element_blank(),
        plot.margin = unit(c(0,0,0,0),"mm"),
        plot.background = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks.length = unit(0, "pt"))

# Custom color palette for Sumaila subsidy types
goodColors <- rev(brewer.pal(3,"Blues"))
names(goodColors) <- levels(subsidy_dat_ordered$type)[1:3]

badColors <- rev(brewer.pal(7, "Reds"))
names(badColors) <- levels(subsidy_dat_ordered$type)[4:10]

ambigColors <- c("purple", "mediumorchid", "violet")
names(ambigColors) <- levels(subsidy_dat_ordered$type)[11:13]

myColors <- c(goodColors, badColors, ambigColors)


## For loop to run top X countries
for(i in 1:length(top_flag_states)){
   
### Step 1: Flag state connectivity data
# Pull connectivity data for only our flag state of interest
flag_dat <- flag_state_mapping_wlines %>%
  dplyr::filter(flag == top_flag_states[i]) 

# Write flag state connectivity data
write_csv(flag_dat, path = paste0(country_dir, top_flag_states[i], "_flag_state_dat.csv"))

### Step 2: Make connectivity map
# Map
map_plot <- ggplot()+
  geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = country_map %>% dplyr::filter(iso3 == top_flag_states[i]), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, white border lines)
  geom_sf(data = EEZ_map %>% dplyr::filter(iso_tr1 == top_flag_states[i]), fill = NA, alpha = 0.5, color = NA, size = 0.1) +
  geom_sf(data = EEZ_map %>% dplyr::filter(mrgid %in% flag_dat$eez_code), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = flag_dat, col = "darkgoldenrod", size = 0.25) + 
  maptheme+
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

# Save map
ggsave(map_plot, filename = paste0(country_dir, top_flag_states[i], "_flag_state_map.png"), width = 10, units = "in")

# Combine map into a one page pdf
sfg_logo_white <- readPNG(here::here("common", "sfg-logo-white.png"))
logo_white <- rasterGrob(sfg_logo_white, interpolate=TRUE, vjust = 0.8, hjust = 0.6)

title1 <- textGrob(paste0("Global network of distant-water fishing\nFlag state: ", top_flag_states_names[i]), gp = gpar(fontsize=16, fontface="bold", lineheight=1, col = "white", fontfamily = "Helvetica"), hjust = 0.55, vjust = 1)

caption1 <- textGrob(paste0("This map shows the global range of distant-water fishing effort for vessels flagged to ", top_flag_states_names[i], ". Lines connect the flag state (pink) \nwith all foreign EEZs (blue) in which vessels flagged to that state fished in 2018. Data were taken from Global Fishing Watch (2018)."), gp = gpar(fontsize = 10, col = "white", fontfamily = "Helvetica"), vjust = 0, hjust = 0.5)

lay1 <- rbind(c(1,4),
              c(2,2),
              c(2,2),
              c(3,3))

# Put together connectivity map
map_page <- grid.arrange(title1, map_plot, caption1, logo_white,
                         layout_matrix = lay1,
                         heights=unit(c(1,1.5,5,1), c("in")), 
                         widths=unit(c(8,3), "in"))
out1 <- cowplot::ggdraw(map_page) + 
  theme(plot.background = element_rect(fill="grey27", color = NA))

# Save connectivity map
ggsave(out1, filename = paste0(country_dir, top_flag_states[i], "_map_page.pdf"), width = 11, height = 8.5, units = "in")

### Step 3: Make fisheries subsidies summary plot(s) 
# Subsidies by subtype plot
flag_subsidy_dat <- subsidy_dat_ordered %>%
  dplyr::filter(iso3 == top_flag_states[i]) %>%
  na.omit()

if(nrow(flag_subsidy_dat) > 0){
  
  # Filter color scale to only use those for subsidy types represented by that country
  filtered_colors <- myColors[names(myColors) %in% unique(flag_subsidy_dat$type)]
  
  # Make plot
  subsidy_plot <- ggplot(flag_subsidy_dat, aes(x = category, y = value/1e6, fill = type))+
    geom_bar(stat = "identity")+
    scale_fill_manual(name = "Subsidy Type", values = filtered_colors, labels = unique(flag_subsidy_dat$type))+
    theme_bw()+
    coord_flip()+
    scale_y_continuous(expand = c(0,0), labels = scales::comma)+
    labs(x = "", y = "Est. fisheries subsidies (2018 $USD, millions)")
  
  # Save plot as png
  ggsave(subsidy_plot, filename = paste0(country_dir, top_flag_states[i], "_subsidy_plot.png"), width = 10, height = 6, units = "in")
  
  # Make one page pdf of subsidy/other statistics
  sfg_logo_black <- readPNG(here::here("common", "sfg-logo-black.png"))
  logo_black <- rasterGrob(sfg_logo_black, interpolate=TRUE, vjust = 0.8, hjust = 0.6)

  title2 <- textGrob(paste0("Global network of distant-water fishing\nFlag state: ", top_flag_states_names[i]), gp = gpar(fontsize=16, fontface="bold", lineheight=1, col = "black", fontfamily = "Helvetica"), hjust = 0.55, vjust = 1)
  
  dw_summary <- textGrob(
    paste0("Number of distant-water vessels: ", format(flag_state_ranking_top$total_vessels[i], big.mark = ","), 
           "  |  Rank: ", flag_state_ranking_top$vessel_rank[i],
           "\nNumber of EEZs fished: ", length(unique(flag_dat$eez_code)), 
           "  |  Rank: ", flag_state_combinations_ranking$eez_rank[flag_state_combinations_ranking$flag == top_flag_states[i]],
           "\nTotal distant-water capacity (KW): ", format(round(flag_state_ranking_top$total_capacity[i]), big.mark = ","),
           "  |  Rank: ", flag_state_ranking_top$capacity_rank[i],
           "\nTotal distant-water fishing effort (hours): ", format(round(flag_state_ranking_top$total_fishing_hours[i]), big.mark = ","),
           "  |  Rank: ", flag_state_ranking_top$fishing_hours_rank[i],
           "\nTotal distant-water fishing effort (KWh): ", format(round(flag_state_ranking_top$total_fishing_KWh), big.mark = ","),
           "  |  Rank: ", flag_state_ranking_top$fishing_KWh_rank[i]), just = "left", x = unit(0.14, "npc")
  )

  caption2 <- textGrob(paste0("This figure shows fisheries subsides provided by ", top_flag_states_names[i], " in 2018 $USD. Subsidies are grouped into three types: neutral (purples), capacity-enhancing (reds), \nand beneficial (blues) based on their generalized effects. Data are updated estimates from those found in Sumaila et al. (2016)."), gp = gpar(fontsize = 10, col = "black", fontfamily = "Helvetica"), vjust = 0, hjust = 0.5)

  # Layout matrix
  lay <- rbind(c(1,5),
               c(2,2),
               c(3,3),
               c(4,4))
  
  # Create info/summary page
info_page <- grid.arrange(title2, dw_summary, subsidy_plot, caption2, logo_black, 
                          layout_matrix = lay, 
                          heights = unit(c(1,1.5,5,1), "in"), 
                          widths = unit(c(8,3), "in"))

out2 <- cowplot::ggdraw(info_page) +
  theme(plot.background = element_rect(fill="white", color = NA))

# Save summary page
ggsave(out2, filename = paste0(country_dir, top_flag_states[i], "_info_page.pdf"), width = 11, height = 8.5, units = "in")
  
# Save both plots into one pdf
  out_flag_state <- marrangeGrob(grobs = list(out1, out2), nrow = 1, ncol = 1, top = NULL)
  ggsave(out_flag_state, filename = paste0(country_dir, top_flag_states[i], "_combined.pdf"), width = 11, height = 8.5, units = "in")
}

}

```

# Identify top DW fishing fleets by EEZ

We identify the top `r number_of_top_countries_eez` EEZs in which DW fleets fish. We consider the following metrics:
- Number of fishing vessels partaking in DW fishing
- Total number of DW fishing hours
- Total number of DW fishing KWh

```{r}
# Mutate totals by EEZ
## It seems that there is no fishing in Belize's EEZ in this data set
#BLZ <- dw_effort %>% 
  #filter(eez_territory_iso3 == "BLZ")

EEZ_ranking <- dw_effort_final %>% 
  dplyr::filter(year == analysis_year) %>%
  group_by(eez_code, eez_name, eez_territory_iso3, eez_sovereign_iso3, ssvid) %>%
  summarize(engine_power_kw = unique(engine_power_kw),
            fishing_hours = sum(fishing_hours_year_eez, na.rm = T),
            fishing_KWh = sum(fishing_KWh, na.rm = T)) %>%
  ungroup() %>%
  group_by(eez_code, eez_name, eez_territory_iso3, eez_sovereign_iso3) %>%
  summarize(total_vessels = n_distinct(ssvid),
            total_capacity = sum(engine_power_kw, na.rm = T),
            total_fishing_hours = sum(fishing_hours, na.rm = T),
            total_fishing_KWh = sum(fishing_KWh, na.rm = T)) %>% 
  arrange(desc(total_vessels)) %>%
  ungroup() %>%
  mutate(vessel_rank = dense_rank(desc(total_vessels)),
         capacity_rank = dense_rank(desc(total_capacity)),
         fishing_hours_rank = dense_rank(desc(total_fishing_hours)),
         fishing_KWh_rank = dense_rank(desc(total_fishing_KWh))) %>%
  mutate(avg_rank = rowMeans(select(., c(vessel_rank, capacity_rank, fishing_hours_rank, fishing_KWh_rank))))

# Identify top flag states based on average ranking
EEZ_ranking_top <- EEZ_ranking %>%
 top_n(-number_of_top_countries_eez, wt = avg_rank)

write_csv(EEZ_ranking_top, paste0(table_dir, "top_", number_of_top_countries_eez, "_EEZs_avg_", analysis_year, ".csv"))

# Just in case - let's make top lists for each category as well
# Vessels
write_csv(EEZ_ranking %>%
            top_n(-number_of_top_countries_eez, wt = vessel_rank), 
          paste0(table_dir, "top_", number_of_top_countries_eez, "_EEZs_vessels_", analysis_year, ".csv"))

# Total capacity
write_csv(EEZ_ranking %>%
            top_n(-number_of_top_countries_eez, wt = capacity_rank), 
          paste0(table_dir, "top_", number_of_top_countries_eez, "_EEZs_capacity_", analysis_year, ".csv"))

# Fishing hours
write_csv(EEZ_ranking %>%
            top_n(-number_of_top_countries_eez, wt = fishing_hours_rank), 
          paste0(table_dir, "top_", number_of_top_countries_eez, "_EEZs_fishing_hours_", analysis_year, ".csv"))

# Fishing KWh
write_csv(EEZ_ranking %>%
            top_n(-number_of_top_countries_eez, wt = fishing_KWh_rank), 
          paste0(table_dir, "top_", number_of_top_countries_eez, "_EEZs_fishing_KWh_", analysis_year, ".csv"))

```


```{r}
top_eezs <- EEZ_ranking_top$eez_code
top_eez_names <- EEZ_ranking_top$eez_territory_iso3
top_eez_names_long <- EEZ_ranking_top$eez_name
top_eez_names_long[which(top_eezs == "8389")] <- "Falkland Islands Exclusive Economic Zone: UK / Argentina"


##EEZ combinations top 10
eez_combinations <- dw_effort_final %>%
  dplyr::filter(eez_code %in% top_eezs) %>%
  distinct(eez_code = as.numeric(eez_code), eez_territory_iso3, flag) %>%
  arrange(eez_code)


```

In order to make our connection plots, we again need the centroids of each EEZ and flag state, which we match to each of our top EEZs, as well as to all flag states from which vessels are fishing in each EEZ.

```{r}

## eez mapping top 10
eez_mapping <- eez_combinations %>%
  left_join(centroid_coordinates_EEZ_edited, by = c("eez_code" = "eez_code")) %>%
  left_join(centroid_coordinates_flag_edited, by = c("flag" = "flag")) 

# There are some flag states for which we need to manually assign centroids (mostly small island states not included in the world map because they don't show up)
# Tuvalu (TUV)
eez_mapping$flag_lon[eez_mapping$flag == "TUV"] <- centroid_coordinates_EEZ_edited$eez_lon[centroid_coordinates_EEZ_edited$eez_code == 8326]
eez_mapping$flag_lat[eez_mapping$flag == "TUV"] <- centroid_coordinates_EEZ_edited$eez_lat[centroid_coordinates_EEZ_edited$eez_code == 8326]

# Réunion (REU)
eez_mapping$flag_lon[eez_mapping$flag == "REU"] <- centroid_coordinates_EEZ_edited$eez_lon[centroid_coordinates_EEZ_edited$eez_code == 8338]
eez_mapping$flag_lat[eez_mapping$flag == "REU"] <- centroid_coordinates_EEZ_edited$eez_lat[centroid_coordinates_EEZ_edited$eez_code == 8338]

# Bonaire, Sint Eustatius and Saba (BES)
eez_mapping$flag_lon[eez_mapping$flag == "BES"] <- centroid_coordinates_EEZ_edited$eez_lon[centroid_coordinates_EEZ_edited$eez_code == 26520]
eez_mapping$flag_lat[eez_mapping$flag == "BES"] <- centroid_coordinates_EEZ_edited$eez_lat[centroid_coordinates_EEZ_edited$eez_code == 26520]

# Guatemala - old code (GCA)
eez_mapping$flag_lon[eez_mapping$flag == "GCA"] <- centroid_coordinates_flag_edited$flag_lon[centroid_coordinates_flag_edited$flag == "GTM"]
eez_mapping$flag_lat[eez_mapping$flag == "GCA"] <- centroid_coordinates_flag_edited$flag_lat[centroid_coordinates_flag_edited$flag == "GTM"]

```


```{r}
# We then make our lines from each EEZ going to all of the countries fishing there. 
eez_mapping_wlines <- eez_mapping %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(eez_mapping) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326) #%>% 
  #st_transform(flag_state_mapping, crs = '+proj=robin +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs')

```


```{r}
## All EEZ connections

##EEZ combinations all
eez_combinations_all <-dw_effort_final %>% 
  distinct(eez_code = as.numeric(eez_code), eez_territory_iso3, flag) %>%
  arrange(eez_code)

## eez mapping top 10
eez_mapping_all <- eez_combinations_all %>%
  left_join(centroid_coordinates_EEZ_edited, by = c("eez_code" = "eez_code")) %>%
  left_join(centroid_coordinates_flag_edited, by = c("flag" = "flag")) 

# There are some flag states for which we need to manually assign centroids (mostly small island states not included in the world map because they don't show up)
# Tuvalu (TUV)
eez_mapping_all$flag_lon[eez_mapping_all$flag == "TUV"] <- centroid_coordinates_EEZ_edited$eez_lon[centroid_coordinates_EEZ_edited$eez_code == 8326]
eez_mapping_all$flag_lat[eez_mapping_all$flag == "TUV"] <- centroid_coordinates_EEZ_edited$eez_lat[centroid_coordinates_EEZ_edited$eez_code == 8326]

# Réunion (REU)
eez_mapping_all$flag_lon[eez_mapping_all$flag == "REU"] <- centroid_coordinates_EEZ_edited$eez_lon[centroid_coordinates_EEZ_edited$eez_code == 8338]
eez_mapping_all$flag_lat[eez_mapping_all$flag == "REU"] <- centroid_coordinates_EEZ_edited$eez_lat[centroid_coordinates_EEZ_edited$eez_code == 8338]

# Bonaire, Sint Eustatius and Saba (BES)
eez_mapping_all$flag_lon[eez_mapping_all$flag == "BES"] <- centroid_coordinates_EEZ_edited$eez_lon[centroid_coordinates_EEZ_edited$eez_code == 26520]
eez_mapping_all$flag_lat[eez_mapping_all$flag == "BES"] <- centroid_coordinates_EEZ_edited$eez_lat[centroid_coordinates_EEZ_edited$eez_code == 26520]

# Guatemala - old code (GCA)
eez_mapping_all$flag_lon[eez_mapping_all$flag == "GCA"] <- centroid_coordinates_flag_edited$flag_lon[centroid_coordinates_flag_edited$flag == "GTM"]
eez_mapping_all$flag_lat[eez_mapping_all$flag == "GCA"] <- centroid_coordinates_flag_edited$flag_lat[centroid_coordinates_flag_edited$flag == "GTM"]

# We then make our lines from each EEZ going to all of the countries fishing there. 
eez_mapping_wlines_all <- eez_mapping_all %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(eez_mapping_all) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326) #%>% 
  #st_transform(flag_state_mapping, crs = '+proj=robin +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs')

```


```{r}

## For loop to run top EEZs
for(i in 1:length(top_eezs)){

eez_dat <- eez_mapping_wlines %>%
  dplyr::filter(eez_code == top_eezs[i]) 

# Write EEZ data
write_csv(eez_dat, path = paste0(eez_dir, top_eezs[i], "_", top_eez_names[i] , "_EEZ_dat.csv"))

# Make EEZ connection plot
eez_map <- ggplot()+
  geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = country_map %>% dplyr::filter(iso3 %in% eez_dat$flag), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = EEZ_map %>% dplyr::filter(mrgid == top_eezs[i]), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = eez_dat, col = "darkgoldenrod", size = 0.25) +
  maptheme+
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

#plot_map <- plot_map + coord_sf("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")

#plot_map pngs
ggsave(eez_map, filename = paste0(eez_dir, top_eezs[i], "_", top_eez_names[i], "_EEZ_connectivity_map.png"), width = 10, units = "in")

# Combine map into a one page pdf
title3 <- textGrob(paste0("Global network of distant-water fishing\nEEZ: ", top_eez_names_long[i]), gp = gpar(fontsize=16, fontface="bold", lineheight=1, col = "white", fontfamily = "Helvetica"), hjust = 0.55, vjust = 1)

caption3 <- textGrob(paste0("This map shows the global origins of distant-water vessels fishing in the ", top_eez_names_long[i], ". Lines connect the EEZ (blue) \nwith all foreign countries (pink) from which vessels fishing in that EEZ in 2018 are flagged. Data were taken from Global Fishing Watch (2018)."), gp = gpar(fontsize = 10, col = "white", fontfamily = "Helvetica"), vjust = 0, hjust = 0.5)

lay3 <- rbind(c(1,4),
              c(2,2),
              c(2,2),
              c(3,3))

# Put together connectivity map
eez_page <- grid.arrange(title3, eez_map, caption3, logo_white, 
                         layout_matrix = lay3,
                         heights=unit(c(1,1.5,5,1), c("in")), 
                         widths=unit(c(8.25,2.75), "in"))
out3 <- cowplot::ggdraw(eez_page) + 
  theme(plot.background = element_rect(fill="grey27", color = NA))

# Save connectivity map
ggsave(out3, filename = paste0(eez_dir, top_eezs[i], "_", top_eez_names[i], "_map_page.pdf"), width = 11, height = 8.5, units = "in")

### Step 2 - make heat maps
eezmaptheme <- theme_minimal()+
  theme(plot.background = element_rect(fill = "grey27", color = NA),
        panel.background = element_rect(fill = "grey27", color = NA),
        panel.grid.major = element_line(colour = "grey27"),
        text = element_text(color = "white"),
        plot.title = element_text(hjust = 0.5),
        panel.border = element_rect(color = "white", fill = NA),
        plot.margin = margin(t = 0, r = 0.1, b = 0, l = 0, unit = "cm"),
        legend.margin = margin(t = 0.1, r = 0, b = 0.1, l = 0, unit = "cm"),
        legend.position = "bottom",
        legend.box = "horizontal",
        axis.text = element_text(color = "white"))

# Pull data from GFW if necessary
 if(rerun_gfw == T){
    # What bin size do we want to use (degrees)?  
    bin_size <- 0.1

  sql3 <- paste0(
  "WITH
  selected_vi AS (
    SELECT
       year,
       ssvid,
       best.best_engine_power_kw AS engine_power_kw,
       best.best_flag AS flag
    FROM
       `world-fishing-827.gfw_research.vi_ssvid_byyear_v20190430`
    WHERE
       on_fishing_list_best
       AND activity.offsetting IS FALSE),
   
  eez_info AS (
     SELECT
       EXTRACT(year FROM _partitiontime) year,
       if(ARRAY_LENGTH(regions.eez)=0, '0000', regions.eez[ordinal(1)]) eez_code,
       ssvid,
       FLOOR(lat/", bin_size,") * ", bin_size, " + ", bin_size/2, " AS lat_cen,
       FLOOR(lon/", bin_size, ") * ", bin_size, " + ", bin_size/2, " AS lon_cen,
       SUM(hours) AS fishing_hours
     FROM
       `world-fishing-827.gfw_research.pipe_production_b_fishing`
     WHERE
       nnet_score2 > .5
       AND seg_id IN (
          SELECT
            seg_id
          FROM
            `world-fishing-827.gfw_research.pipe_production_b_segs`
          WHERE
            good_seg)
    GROUP BY
      year,
      eez_code,
      ssvid,
      lat_cen,
      lon_cen
    HAVING
      year = ", analysis_year, 
      " AND eez_code = '", as.character(top_eezs[i]), "')
      
 SELECT
    year,
    eez_code,
    flag,
    lat_cen,
    lon_cen,
    SUM(a.fishing_hours) as fishing_hours,
    SUM(a.fishing_hours * b.engine_power_kw) as fishing_KWh,
    SUM(a.fishing_hours * b.engine_power_kw * c.subs_per_fishing_KWh) as subs
  FROM
    eez_info a
  LEFT JOIN
    selected_vi b
  USING
    (year,
    ssvid)
  LEFT JOIN
    `ucsb-gfw.subsidy_atlas.subsidy_rates_flag` c
  USING
    (flag)
  GROUP BY
    year,
    eez_code,
    flag,
    lat_cen,
    lon_cen
  HAVING
    fishing_hours > 1"
  )

  eez_table <- bq_table(project = ucsb_project, table = paste0("fishing_effort_", top_eezs[i]), dataset = "subsidy_atlas") 

  if(bq_table_exists(eez_table) == FALSE){
    bq_table(project = ucsb_project, table = paste0("fishing_effort_", top_eezs[i]), dataset = "subsidy_atlas") %>%
      bq_table_create()
  }else{
    bq_table(project = ucsb_project, table = paste0("fishing_effort_", top_eezs[i]), dataset = "subsidy_atlas") %>%
      bq_table_delete()
  }

  eez_effort <- bq_project_query(ucsb_project, sql3, destination_table = bq_table(project = ucsb_project, table = paste0("fishing_effort_", top_eezs[i]), dataset = "subsidy_atlas"), use_legacy_sql = FALSE, allowLargeResults = TRUE) %>%
    bq_table_download(max_results = Inf)

  write_csv(eez_effort, path = paste0(eez_dir, top_eezs[i], "_", top_eez_names[i], "_EEZ_effort_subs_by_flag.csv"))

  # Load local data instead of rerunning global fishing watch pull 
  } else{
  
  eez_effort <- read_csv(paste0(eez_dir, top_eezs[i], "_", top_eez_names[i], "_EEZ_effort_subs_by_flag.csv"), col_types = "iccnnnnn")
    
  }

  ### Make Plots 
  # Get quantiles of data for scale limits
  eez_effort_aggregated <- eez_effort %>%
    group_by(year, eez_code, lon_cen, lat_cen) %>%
    summarize(fishing_hours = sum(fishing_hours, na.rm = T),
              fishing_KWh = sum(fishing_KWh, na.rm = T),
              subs = sum(subs, na.rm = T)) %>%
    mutate(subsidy_intensity = subs/fishing_KWh)
  
  # Quantiles
  intensity_quantile <- quantile(eez_effort_aggregated$subsidy_intensity, probs = c(0.01, 0.05, 0.95, 0.99), na.rm = T)
  scale_labels <- round(seq(round(intensity_quantile[1], 1), round(intensity_quantile[4], 1), length.out = 5), 1)
  
  # Set map limits for filtering global country map and eez map appropriately
  x_lim <- c(min(eez_effort_aggregated$lon_cen) - 0.5, max(eez_effort_aggregated$lon_cen) + 0.5)
  y_lim <- c(min(eez_effort_aggregated$lat_cen) - 0.5, max(eez_effort_aggregated$lat_cen) + 0.5)
  
  
  # Map of subsidy intensity
  eez_subsidy_plot <- ggplot()+
    geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.5)+ # world EEZs (transparent, light grey border lines)
    geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.5)+ # world countries (dark grey, white border lines)
    geom_raster(data = eez_effort_aggregated, aes(x = lon_cen, y = lat_cen, fill = subsidy_intensity))+
    eezmaptheme +
    scale_fill_viridis_c(na.value = NA, name = "Subsidy intensity \n(2018 $USD/KWh)", 
                         limits=c(round(intensity_quantile[1],1)-round(intensity_quantile[1],1)*0.01, round(intensity_quantile[4], 1) + round(intensity_quantile[4], 1)*0.01), 
                         labels=scale_labels,
                         breaks=scale_labels,
                         oob=scales::squish)+
    labs(x = "", y = "")+
    coord_sf(xlim = x_lim, ylim = y_lim)+
    guides(fill = guide_colorbar(title.position = "bottom", title.hjust = 0.5, barwidth = 18))+
    scale_x_continuous(expand = c(0,0))+
    scale_y_continuous(expand = c(0,0))
  
  # Labels for the log scale 
  eez_effort_plot <- ggplot()+
    geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.5)+ # world EEZs (transparent, light grey border lines)
    geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.5)+ # world countries (dark grey, white border lines)
    geom_raster(data = eez_effort_aggregated, aes(x = lon_cen, y = lat_cen, fill = fishing_KWh))+
    eezmaptheme +
    scale_fill_viridis_c(na.value = NA, option = "A", name = "Fishing effort \n(KWh)", trans = log10_trans(), labels = comma)+
    labs(x = "", y = "")+
    coord_sf(xlim = x_lim, ylim = y_lim) +
    guides(fill = guide_colorbar(title.position = "bottom", title.hjust = 0.5, barwidth = 18))+
    scale_x_continuous(expand = c(0,0))+
    scale_y_continuous(expand = c(0,0))

 
  # Combined plot  
  logo_white2 <- rasterGrob(sfg_logo_white, interpolate=TRUE, vjust = 0.8, hjust = 0.3)
  
title4 <- textGrob(paste0("Global network of distant-water fishing\nEEZ: ", top_eez_names_long[i]), gp = gpar(fontsize=16, fontface="bold", lineheight=1, col = "white", fontfamily = "Helvetica"), hjust = 0.55, vjust = 1)

caption4 <- textGrob(paste0("These maps show distant-water fishing effort (left, KWh) and subsidy intensity (right, 2018 $USD/KWh) in the ", top_eez_names_long[i], ". \nBoth fishing effort and subsidy intensity are aggregated by 0.1 degree latitude/longitude. Data were taken from Global Fishing Watch (2018)."), gp = gpar(fontsize = 10, col = "white", fontfamily = "Helvetica"), vjust = 0, hjust = 0.5)

  if(top_eez_names[i] == "RUS"){
    
    lay4 <- rbind(c(1,1,1,5),
              c(NA,NA,NA,NA),
              c(2,2,2,2),
              c(3,3,3,3),
              c(4,4,4,4))
    
    
  } else{
    
    lay4 <- rbind(c(1,1,1,5),
              c(NA,NA,NA,NA),
              c(2,2,3,3),
              c(2,2,3,3),
              c(4,4,4,4))
    
  }

# Put together connectivity map
page4 <- grid.arrange(title4, eez_effort_plot, eez_subsidy_plot, caption4, logo_white, 
                         layout_matrix = lay4,
                         heights=unit(c(1,0.5,3,3,1), c("in")),
                         widths=unit(c(2.75,2.75,2.75,2.75), "in"))
out4 <- cowplot::ggdraw(page4) + 
  theme(plot.background = element_rect(fill="grey27", color = NA))

# Save connectivity map
ggsave(out4, filename = paste0(eez_dir, top_eezs[i], "_", top_eez_names[i], "_effort_page.pdf"), width = 11, height = 8.5, units = "in")

# Save both plots into one pdf
  out_eez <- marrangeGrob(grobs = list(out3, out4), nrow = 1, ncol = 1, top = NULL)
  ggsave(out_eez, filename = paste0(eez_dir, top_eezs[i], "_", top_eez_names[i], "_combined.pdf"), width = 11, height = 8.5, units = "in")

}
```

```{r Making ACP EEZ Connectivity Maps}
#top_eezs <- EEZ_ranking_top$eez_code
#top_eez_names <- EEZ_ranking_top$eez_territory_iso3
#top_eez_names_long <- EEZ_ranking_top$eez_name
#top_eez_names_long[which(top_eezs == "8389")] <- "Falkland Islands Exclusive Economic Zone: UK / Argentina"


#eez_combinations <- dw_effort_final %>%
  #dplyr::filter(eez_code %in% top_eezs) %>%
  #distinct(eez_code = as.numeric(eez_code), eez_territory_iso3, flag) %>%
  #arrange(eez_code)
##########

ACP_codes <- read_csv("ACP_eez_codes.csv") %>% 
  filter(eez_id != "N/A")

ACP_eezs_filter <- EEZ_ranking %>% 
  filter(eez_code %in% ACP_codes$eez_id) 
ACP_eez_names_filter <- EEZ_ranking %>% 
  filter(eez_territory_iso3 %in% ACP_codes$territory_iso3) %>% 
  filter(!eez_code %in% c("21797", "21798", "33176", "33185", "48964", "48969")) ## Filte#ACP_eez_names_long <- EEZ_ranking %>% 
  #filter(eez_code %in% ACP_codes$eez_id)

ACP_eezs_filter <- merge (ACP_eezs_filter, ACP_eez_names_filter , all.x=T, all.y=T)


ACP_eezs <- ACP_eezs_filter$eez_code
ACP_eez_names <- ACP_eezs_filter$eez_territory_iso3


ACP_eez_combinations <- dw_effort_final %>%
  filter(eez_territory_iso3 %in% ACP_eezs_filter$eez_territory_iso3) %>%
  distinct(eez_code = as.numeric(eez_code), flag, eez_territory_iso3) %>%
  arrange(eez_code)


ACP_eez_mapping <- ACP_eez_combinations %>%
  left_join(centroid_coordinates_EEZ_edited, by = c("eez_code" = "eez_code")) %>%
  left_join(centroid_coordinates_flag_edited, by = c("flag" = "flag")) 

ACP_eez_mapping_wlines <- ACP_eez_mapping %>%
  select(flag_lon, flag_lat, eez_lon, eez_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .) %>% 
  bind_cols(ACP_eez_mapping) %>%
  select(everything(), geometry) %>% 
  st_segmentize(units::set_units(100,km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326) #%>% 
  #st_transform(flag_state_mapping, crs = '+proj=robin +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs')

write_csv(ACP_eez_mapping_wlines, path = paste0(ACP_dir, "ACP_eez_mapping_wlines.csv"))
write_csv(ACP_eez_mapping_wlines, path = paste0(ACP_app_dir, "ACP_eez_mapping_wlines.csv"))
#st_write(ACP_eez_mapping_wlines, paste0(ACP_app_dir, "ACP_eez_mapping_wlines.shp"))


## For loop to run ACP EEZs
for(i in 1:length(ACP_eezs)){

  
ACP_eez_dat <- ACP_eez_mapping_wlines %>%
  dplyr::filter(eez_code == ACP_eezs[i]) 

# Write ACP EEZ data
write_csv(ACP_eez_dat, path = paste0(ACP_dir, ACP_eezs[i], "_", ACP_eez_names[i] , "_EEZ_dat.csv"))
write_csv(ACP_eez_dat, path = paste0(ACP_app_dir, ACP_eezs[i], "_", ACP_eez_names[i] , "_EEZ_dat.csv")) #ACP App directory

#write_csv(eez_dat, path = paste0(eez_dir, top_eezs[i], "_", top_eez_names[i] , "_EEZ_dat.csv"))

# Make EEZ connection plot
ACP_eez_map <- ggplot()+
  geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = country_map %>% dplyr::filter(iso3 %in% ACP_eez_dat$flag), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = EEZ_map %>% dplyr::filter(mrgid == ACP_eezs[i]), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = ACP_eez_dat, col = "darkgoldenrod", size = 0.25) +
  maptheme+
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

#plot_map <- plot_map + coord_sf("+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")

#plot_map pngs
ggsave(ACP_eez_map, filename = paste0(ACP_dir, ACP_eezs[i], "_", ACP_eez_names[i], "_", "ACP_EEZ_connectivity_map.png"), width = 10, units = "in")

ggsave(ACP_eez_map, filename = paste0(ACP_app_dir, ACP_eezs[i], "_", ACP_eez_names[i], "_", "ACP_EEZ_connectivity_map.png"), width = 10, units = "in") #ACP App directory

} #Add when just making connectivity maps



```


```{r}

### Step 2 - make heat maps

# Pull data from GFW if necessary
for(i in 1:length(ACP_eezs)){

 if(rerun_gfw == T){
    # What bin size do we want to use (degrees)?  
    bin_size <- 0.1

  sql3 <- paste0(
  "WITH
  selected_vi AS (
    SELECT
       year,
       ssvid,
       best.best_engine_power_kw AS engine_power_kw,
       best.best_flag AS flag
    FROM
       `world-fishing-827.gfw_research.vi_ssvid_byyear_v20190430`
    WHERE
       on_fishing_list_best
       AND activity.offsetting IS FALSE),
   
  eez_info AS (
     SELECT
       EXTRACT(year FROM _partitiontime) year,
       if(ARRAY_LENGTH(regions.eez)=0, '0000', regions.eez[ordinal(1)]) eez_code,
       ssvid,
       FLOOR(lat/", bin_size,") * ", bin_size, " + ", bin_size/2, " AS lat_cen,
       FLOOR(lon/", bin_size, ") * ", bin_size, " + ", bin_size/2, " AS lon_cen,
       SUM(hours) AS fishing_hours
     FROM
       `world-fishing-827.gfw_research.pipe_production_b_fishing`
     WHERE
       nnet_score2 > .5
       AND seg_id IN (
          SELECT
            seg_id
          FROM
            `world-fishing-827.gfw_research.pipe_production_b_segs`
          WHERE
            good_seg)
    GROUP BY
      year,
      eez_code,
      ssvid,
      lat_cen,
      lon_cen
    HAVING
      year = ", analysis_year, 
      " AND eez_code = '", as.character(ACP_eezs[i]), "')
      
 SELECT
    year,
    eez_code,
    flag,
    lat_cen,
    lon_cen,
    SUM(a.fishing_hours) as fishing_hours,
    SUM(a.fishing_hours * b.engine_power_kw) as fishing_KWh,
    SUM(a.fishing_hours * b.engine_power_kw * c.subs_per_fishing_KWh) as subs
  FROM
    eez_info a
  LEFT JOIN
    selected_vi b
  USING
    (year,
    ssvid)
  LEFT JOIN
    `ucsb-gfw.subsidy_atlas.subsidy_rates_flag` c
  USING
    (flag)
  GROUP BY
    year,
    eez_code,
    flag,
    lat_cen,
    lon_cen
  HAVING
    fishing_hours > 1"
  )

  eez_table <- bq_table(project = ucsb_project, table = paste0("fishing_effort_", ACP_eezs[i]), dataset = "subsidy_atlas") 

  if(bq_table_exists(eez_table) == FALSE){
    bq_table(project = ucsb_project, table = paste0("fishing_effort_", ACP_eezs[i]), dataset = "subsidy_atlas") %>%
      bq_table_create()
  }else{
    bq_table(project = ucsb_project, table = paste0("fishing_effort_", ACP_eezs[i]), dataset = "subsidy_atlas") %>%
      bq_table_delete()
  }

  eez_effort <- bq_project_query(ucsb_project, sql3, destination_table = bq_table(project = ucsb_project, table = paste0("fishing_effort_", ACP_eezs[i]), dataset = "subsidy_atlas"), use_legacy_sql = FALSE, allowLargeResults = TRUE) %>%
    bq_table_download(max_results = Inf)

  write_csv(eez_effort, path = paste0(ACP_dir, ACP_eezs[i], "_", ACP_eez_names[i], "_EEZ_effort_subs_by_flag.csv"))

  # Load local data instead of rerunning global fishing watch pull 
  } else{
  
  #eez_effort_ACP <- read_csv(paste0(ACP_dir, ACP_eezs[i], "_", ACP_eez_names[i], "_EEZ_effort_subs_by_flag.csv"), col_types = "iccnnnnn")
    
  }

  ### Make Plots 
  # Get quantiles of data for scale limits
  eez_effort_aggregated <- eez_effort %>%
    group_by(year, eez_code, lon_cen, lat_cen) %>%
    summarize(fishing_hours = sum(fishing_hours, na.rm = T),
              fishing_KWh = sum(fishing_KWh, na.rm = T),
              subs = sum(subs, na.rm = T)) %>%
    mutate(subsidy_intensity = subs/fishing_KWh)
  
  # Quantiles
  intensity_quantile <- quantile(eez_effort_aggregated$subsidy_intensity, probs = c(0.01, 0.05, 0.95, 0.99), na.rm = T)
  scale_labels <- round(seq(round(intensity_quantile[1], 1), round(intensity_quantile[4], 1), length.out = 5), 1)
  
  # Set map limits for filtering global country map and eez map appropriately
  x_lim <- c(min(eez_effort_aggregated$lon_cen) - 0.5, max(eez_effort_aggregated$lon_cen) + 0.5)
  y_lim <- c(min(eez_effort_aggregated$lat_cen) - 0.5, max(eez_effort_aggregated$lat_cen) + 0.5)
  
  
  # Map of subsidy intensity
  eez_subsidy_plot <- ggplot()+
    geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.5)+ # world EEZs (transparent, light grey border lines)
    geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.5)+ # world countries (dark grey, white border lines)
    geom_raster(data = eez_effort_aggregated, aes(x = lon_cen, y = lat_cen, fill = subsidy_intensity))+
    eezmaptheme +
    scale_fill_viridis_c(na.value = NA, name = "Subsidy intensity \n(2018 $USD/KWh)", 
                         limits=c(round(intensity_quantile[1],1)-round(intensity_quantile[1],1)*0.01, round(intensity_quantile[4], 1) + round(intensity_quantile[4], 1)*0.01), 
                         labels=scale_labels,
                         breaks=scale_labels,
                         oob=scales::squish)+
    labs(x = "", y = "")+
    coord_sf(xlim = x_lim, ylim = y_lim)+
    guides(fill = guide_colorbar(title.position = "bottom", title.hjust = 0.5, barwidth = 18))+
    scale_x_continuous(expand = c(0,0))+
    scale_y_continuous(expand = c(0,0))
  
  # Labels for the log scale 
  eez_effort_plot <- ggplot()+
    geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.5)+ # world EEZs (transparent, light grey border lines)
    geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.5)+ # world countries (dark grey, white border lines)
    geom_raster(data = eez_effort_aggregated, aes(x = lon_cen, y = lat_cen, fill = fishing_KWh))+
    eezmaptheme +
    scale_fill_viridis_c(na.value = NA, option = "A", name = "Fishing effort \n(KWh)", trans = log10_trans(), labels = comma)+
    labs(x = "", y = "")+
    coord_sf(xlim = x_lim, ylim = y_lim) +
    guides(fill = guide_colorbar(title.position = "bottom", title.hjust = 0.5, barwidth = 18))+
    scale_x_continuous(expand = c(0,0))+
    scale_y_continuous(expand = c(0,0))

 
  # Combined plot  
  logo_white2 <- rasterGrob(sfg_logo_white, interpolate=TRUE, vjust = 0.8, hjust = 0.3)
  
title4 <- textGrob(paste0("Global network of distant-water fishing\nEEZ: ", top_eez_names_long[i]), gp = gpar(fontsize=16, fontface="bold", lineheight=1, col = "white", fontfamily = "Helvetica"), hjust = 0.55, vjust = 1)

caption4 <- textGrob(paste0("These maps show distant-water fishing effort (left, KWh) and subsidy intensity (right, 2018 $USD/KWh) in the ", top_eez_names_long[i], ". \nBoth fishing effort and subsidy intensity are aggregated by 0.1 degree latitude/longitude. Data were taken from Global Fishing Watch (2018)."), gp = gpar(fontsize = 10, col = "white", fontfamily = "Helvetica"), vjust = 0, hjust = 0.5)

  if(ACP_eez_names[i] == "RUS"){
    
    lay4 <- rbind(c(1,1,1,5),
              c(NA,NA,NA,NA),
              c(2,2,2,2),
              c(3,3,3,3),
              c(4,4,4,4))
    
    
  } else{
    
    lay4 <- rbind(c(1,1,1,5),
              c(NA,NA,NA,NA),
              c(2,2,3,3),
              c(2,2,3,3),
              c(4,4,4,4))
    
  }

#plot_map pngs
ggsave(eez_subsidy_plot, filename = paste0(ACP_dir, ACP_eezs[i], "_", ACP_eez_names[i], "_", "ACP_EEZ_subsidy_plot.png"), width = 10, units = "in")

ggsave(eez_subsidy_plot, filename = paste0(ACP_app_dir, ACP_eezs[i], "_", ACP_eez_names[i], "_", "ACP_EEZ_subsidy_plot.png"), width = 10, units = "in") #ACP App directory

} #Final close loop

```

```{r}

## ACP CONNECTIONS MAP

ACP_connections_map <- ggplot()+
  geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = country_map %>% dplyr::filter(iso3 %in% ACP_eez_mapping_wlines$flag), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = EEZ_map %>% dplyr::filter(ez_hs_c %in% ACP_eez_names_filter$eez_territory_iso3 ), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = ACP_eez_mapping_wlines, col = "darkgoldenrod", size = 0.25) +
  maptheme+
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

plot(ACP_connections_map)

ggsave(ACP_connections_map, filename = paste0(ACP_app_dir, "_ACP_connections_map.png"), width = 10, units = "in")


```


```{r}
## ALL CONNECTIONS MAP

all_connections_map <- ggplot()+
  geom_sf(data = EEZ_map %>% dplyr::filter(is.na(zone)), fill = NA, color = "grey60", size = 0.1)+ # world EEZs (transparent, light grey border lines)
  geom_sf(data = country_map, fill = "grey2", color = "grey40", size = 0.1)+ # world countries (dark grey, white border lines)
  geom_sf(data = country_map %>% dplyr::filter(iso3 %in% eez_mapping_wlines_all$flag), fill = "darkmagenta", color = "grey40", size = 0.1) + # highlighted flag state (magenta, grey border lines)
  geom_sf(data = EEZ_map %>% dplyr::filter(type != "High seas" ), fill = "slateblue", alpha = 0.5, color = NA, size = 0.1) + # highlighted EEZs (slate blue)
  geom_sf(data = eez_mapping_wlines_all, col = "darkgoldenrod", size = 0.25) +
  maptheme+
  coord_sf(xlim = c(-180,180), ylim = c(-90,90))+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))

plot(all_connections_map)

ggsave(all_connections_map, filename = paste0(ACP_app_dir, "_all_connections_map.png"), width = 10, units = "in")



```

